### 2016-06-17 main.tex
Initial commit

\documentclass[twoside,11pt]{article}

\usepackage{jmlr2e}

% Heading arguments are {volume}{year}{pages}{submitted}{published}{author-full-names}
\jmlrheading{7}{2016}{1-5}{7/16}{-}{Guillaume Lema\^itre, Fernando Nogueira, and Davyid Victor}

% Short headings should be running head and authors last names
\ShortHeadings{A python toolbox to tackle the curse of imbalanced dataset in machine learning}{Lema\^itre, Nogueira, and Victor}
\firstpageno{1}

\begin{document}

\title{A python toolbox to tackle the curse of imbalanced dataset in machine learning}
\author{Guillaume Lema\^itre \email g.lemaitre58@gmail.com \\ \addr{LE2I UMR6306, CNRS, Arts et M\'etiers, Universit\'e Bourgogne Franche-Comt\'e} \\ \addr{12 rue de la Fonderie, 71200 Le Creusot, France} \\ \addr{ViCOROB, Universitat de Girona} \\ \addr{Campus Montilivi, Edifici P4, 17071 Girona, Spain}
        \AND
        Fernando Nogueira \email fmfnogueira@gmail.com \\ \addr{theScore, Inc.} \\ \addr{500 King Street West 4\textsuperscript{th} Floor Toronto, Ontario M5V1L9 Canada}
        \AND
        Dayvid Victor Rodrigues de Oliveira \email victor.dvro@gmail.com \\ \addr{VIISAR Research Group, Centto de Inform\'atica (CIn) - Federal University of Pernambuco (UFPE)} \\ \addr{Av. Prof. Luiz Freire, s/n - Cidade Universitária Recife - PE, 50740-540, Brazil}} 
\editor{-}

\maketitle

\begin{abstract}
\emph{UnbalancedDataset} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
The state-of-the-art methods implemented can be categorized into 4 different sampling strategies: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
The proposed toolbox depends of \emph{numpy}, \emph{scipy}, and \emph{scikit-learn}.
The implementation pattern is identical to the \emph{scikit-learn} API to offer compatibility.
Documentation, unit tests as well as integration tests are provided to allow new developers to contribute.
The toolbox is publicly available in GitHub \url{https://github.io} as well as the documentation \url{https://github.io}.
\end{abstract}

\begin{keywords}
Imbalanced Dataset, Over-Sampling, Under-Sampling, Ensemble Learning, Machine Learning, Python.
\end{keywords}

\section{Introduction}

This problem is frequently referred as ``class imbalance'' problem~\cite{prati2009data} and has been encountered in multiple areas such as telecommunication managements, bioinformatics, fraud detection, and medical diagnosis. 
Imbalanced data substantially compromises the learning process since most of the standard machine learning algorithms expect balanced class distribution or an equal mis-classification cost~\cite{he2009learning}.
Medical data are prone to such drawbacks due to the fact that the portion of diseased samples or patients is far lower than healthy cases.
Furthermore, the detection and classification of minority malignant cases are highly essential so that the sensitivity of developed algorithms need to be maximized.
Consequently, the problem of imbalanced data is usually addressed by employing different techniques which do not impair the topology of the data.

\section{Implemented methods}

Three strategies can be employed to overcome the problem of imbalanced dataset: (i) under-sampling, (ii) over-sampling, (iii) a combination of both, and (iv) ensemble learning.
The following sections give an overview of the techniques used to tackle this issue.

\subsection{Under-sampling}

Considering the problem of imbalanced, under-sampling is performed such that the number of samples of the majority class is reduced to be equal to the number of samples of the minority class.
The following methods are considered to perform such balancing.

\begin{description}
  \item[Random under-sampling] is performed by randomly selecting without replacement a subset of samples from the majority class such that the number of samples is then equal in both minority and majority classes.
  \item[Tomek links] can be used to under-sample the majority class of the original dataset~\cite{tomek1976two}.
Let define a pair of nearest neighbour samples $(x_i, x_j)$ such that their associated class label $y_i \neq y_j$.
The pair $(x_i, x_j)$ is defined as a Tomek link if, by relaxing the class label differentiation constraint, there is no other sample $x_k$ defined as the nearest neighbour of either $x_i$ or $x_j$.
Under-sampling is performed by removing the samples belonging to the majority class and forming a Tomek link.
It can be noted that this under-sampling strategy does not enforce a strict balancing between the majority and the minority classes.
  \item[Cluster centroids method] refers to the use of a $k$-means to cluster the feature space such that $k$ is set to be equal to the number of samples composing the minority class.
Hence, the centroids of these clusters define the new samples of the majority class. 
  \item[NearMiss] offers three different methods to under-sample the majority class~\cite{mani2003knn}.
In NearMiss-1, samples from the majority class are selected such that for each sample, the average distance to the $k$ nearest neighbour samples from the minority class is minimum.
NearMiss-2 diverges from NearMiss-1 by considering the $k$ farthest neighbours samples from the minority class.
In NearMiss-3, a subset $M$ containing samples from the majority class is generated by finding the $m$ nearest neighbours from each sample of the minority class.
Then, samples from the subset $M$ are selected such that for each sample, the average distance to the $k$ nearest neighbour samples from the minority class is maximum.
In our experiment, $k$ and $m$ are fixed to 3.
  \item[Neighbourhood cleaning rule] consists of applying two rules depending on the class of each sample~\cite{laurikkala2001improving}.
Let define $x_i$ as a sample of the dataset with its associated class label $y_i$.
Let define $y_m$ as the class of the majority vote of the $k$ nearest neighbours of the sample $x_i$.
If $y_i$ corresponds to the majority class and $y_i \neq y_m$, $x_i$ is rejected from the final subset.
If $y_i$ corresponds to the minority class and and $y_i \neq y_m$, then the $k$ nearest neighbours are rejected from the final subset.
In our experiment $k$ is fixed to 3.
\end{description}

\subsection{Over-sampling}

In the contrary, the data balancing can be performed by over-sampling in which the new samples belonging to the minority class are generated aiming at equalizing the number of samples in both classes.
Two different methods are considered.
\begin{description}
\item[Random over-sampling] is performed by randomly replicating the samples of the minority class such that the number of samples is equal in both minority and majority classes.
\end{description}
\begin{description}
\item[SMOTE] is a method to generate synthetic samples in the feature space~\cite{chawla2002smote}.
Let define $x_i$ as a sample belonging to the minority class.
Let define $x_{nn}$ as a randomly selected sample from the $k$ nearest neighbours of $x_i$, with $k$ set to 3.
Therefore, a new sample $x_j$ is generated such that $x_j = x_i + \sigma \left( x_{nn} - x_i \right)$, where $\sigma$ is a random number in the interval $\left[0,1\right]$.
Three other variants of this algorithm exist: (i) SMOTE borderline 1, (ii) SMOTE borderline 2, and (iii) SMOTE SVM.
\end{description}

\subsection{Combination of over- and under-sampling}

Subsequently, over-sampling methods can be combined with under-sampling methods to clean the subset created.
In that regard, two different combinations are tested.

\begin{description}
  \item[SMOTE + Tomek links] are combined to clean the samples created using SMOTE~\cite{batista2003balancing}.
SMOTE over-sampling can lead to over-fitting which can be avoided by removing the Tomek links from both majority and minority classes~\cite{prati2009data}.
  \item[SMOTE + edited nearest neighbours] are combined for the same aforementioned reason~\cite{batista2004study}.
\end{description}

\subsection{Ensemble learning}

Under-sampling methods implies that samples of the majority class will be lost during the balancing procedure.
Ensemble methods can offer an alternative to use most of the samples.
In fact, an ensemble of balanced set will be created and used to later train any classifier.
Two methods are available to build such ensemble.

\begin{description}
  \item[Balance cascade]
  \item[Easy ensemble]
\end{description}

% \begin{figure}
%   \centering
%   \hspace*{\fill}
%   \subfigure[]{\label{subfig:clustercentroids}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_cluster_centroids_001.png}} \hfill
%   \subfigure[]{\label{subfig:condensednearestneighbour}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_condensed_nearest_neighbour_001.png}} \hfill
%   \subfigure[]{\label{subfig:editedneasrestneighbours}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_edited_nearest_neighbours_001.png}}
%   \hspace*{\fill}\\
%   \hspace*{\fill}
%   \subfigure[]{\label{subfig:nearmiss1}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_nearmiss_1_001.png}} \hfill
%   \subfigure[]{\label{subfig:nearmiss2}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_nearmiss_2_001.png}} \hfill
%   \subfigure[]{\label{subfig:nearmiss3}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_nearmiss_3_001.png}}
%   \hspace*{\fill}\\
%   \hspace*{\fill}
%   \subfigure[]{\label{subfig:onesidedselection}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_one_sided_selection_001.png}} \hfill
%   \subfigure[]{\label{subfig:neighbourhoodcleaningrule}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_neighbourhood_cleaning_rule_001.png}} \hfill
%   \subfigure[]{\label{subfig:tomeklinks}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_tomek_links_001.png}}
%   \hspace*{\fill}\\
%   \hspace*{\fill}
%   \subfigure[]{\label{subfig:smote}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_smote_001.png}} \hfill
%   \subfigure[]{\label{subfig:smoteborderline1}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_smote_bordeline_1_001.png}} \hfill
%   \subfigure[]{\label{subfig:smoteborderline2}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_smote_bordeline_2_001.png}}
%   \hspace*{\fill}\\
%   \hspace*{\fill}
%   \subfigure[]{\label{subfig:smotesvm}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_smote_svm_001.png}} \hfill
%   \subfigure[]{\label{subfig:smoteenn}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_smote_enn_001.png}} \hfill
%   \subfigure[]{\label{subfig:smotetomek}\includegraphics[width=0.3\linewidth]{sphx_glr_plot_smote_tomek_001.png}}
%   \hspace*{\fill}
%   \caption{Toy examples for the different sampling methods.}
%   \label{fig:methods}
% \end{figure}

\section{Implementation design}

The implementation rely on \emph{numpy}, \emph{scipy}, and \emph{scikit-learn}.
The implementation pattern is identical to the \emph{scikit-learn} API to offer compatibility.
Each class implements 3 main functions inspired from the \emph{scikit-learn} API:
(i) \emph{fit} computes the parameter values which are later needed to transform the data into a balanced set;
(ii) \emph{transform} performs the sampling and return the data with the desired balancing ratio;
and (iii) \emph{fit\_transform} is equivalent of calling the function \emph{fit} follow the function \emph{transform}.

\section{Sustainability and continuous integration}

In order to be sustainable and improved over years, the current toolbox offer a detailed documentation as well as a unit and integration tests.
A set of \emph{getting started} guide, examples, and API documentation is available.
The API documentation is automatically generated using \emph{sphinx} and \emph{numpydoc}.
A set of unit tests are implemented to allow back compatibility and integration of new pull-requests.
Furthermore, automatic continuous integration is also available through Travis CI.
Bugs can be reported through the issue tracker system provided by GitHub.

\begin{description}
  \item[Documentation]
  \item[Unit tests]
  \item[Integration tests]
\end{description}

\section{Conclusion}

\bibliography{bibtex}

\end{document}

### 2016-06-18 main.tex

@@
 % Heading arguments are {volume}{year}{pages}{submitted}{published}{author-full-names}
-\jmlrheading{7}{2016}{1-5}{7/16}{-}{Guillaume Lema\^itre, Fernando Nogueira, and Davyid Victor}
+\jmlrheading{7}{2016}{1-5}{7/16}{-}{Guillaume Lema\^itre, Fernando Nogueira, and Dayvid V. R. Oliveira}
 
 % Short headings should be running head and authors last names
-\ShortHeadings{A python toolbox to tackle the curse of imbalanced dataset in machine learning}{Lema\^itre, Nogueira, and Victor}
+\ShortHeadings{A python toolbox to tackle the curse of imbalanced datasets in machine learning}{Lema\^itre, Nogueira, and Victor}
 \firstpageno{1}
@@
 
-\title{A python toolbox to tackle the curse of imbalanced dataset in machine learning}
-\author{Guillaume Lema\^itre \email g.lemaitre58@gmail.com \\ \addr{LE2I UMR6306, CNRS, Arts et M\'etiers, Universit\'e Bourgogne Franche-Comt\'e} \\ \addr{12 rue de la Fonderie, 71200 Le Creusot, France} \\ \addr{ViCOROB, Universitat de Girona} \\ \addr{Campus Montilivi, Edifici P4, 17071 Girona, Spain}
+\title{A python toolbox to tackle the curse of imbalanced datasets in machine learning}
+\author{Guillaume Lema\^itre \email g.lemaitre58@gmail.com \\ 
+    \addr{LE2I UMR6306, CNRS, Arts et M\'etiers, Universit\'e Bourgogne Franche-Comt\'e} \\ 
+    \addr{12 rue de la Fonderie, 71200 Le Creusot, France} \\ 
+    \addr{ViCOROB, Universitat de Girona} \\ 
+    \addr{Campus Montilivi, Edifici P4, 17071 Girona, Spain}
         \AND
-        Fernando Nogueira \email fmfnogueira@gmail.com \\ \addr{theScore, Inc.} \\ \addr{500 King Street West 4\textsuperscript{th} Floor Toronto, Ontario M5V1L9 Canada}
+        Fernando Nogueira \email fmfnogueira@gmail.com \\ 
+        \addr{theScore, Inc.} \\ 
+        \addr{500 King Street West 4\textsuperscript{th} Floor Toronto, Ontario M5V1L9 Canada}
         \AND
-        Dayvid Victor Rodrigues de Oliveira \email victor.dvro@gmail.com \\ \addr{VIISAR Research Group, Centto de Inform\'atica (CIn) - Federal University of Pernambuco (UFPE)} \\ \addr{Av.
-Prof.
-Luiz Freire, s/n - Cidade Universitária Recife - PE, 50740-540, Brazil}}
+        Dayvid V. R. Oliveira \email dvro@cin.ufpe.br \\ 
+        \addr{VIISAR Research Group, Centro de Inform\'atica - Universidade Federal de Pernambuco} \\ 
+        %\addr{Av. Prof. Luiz Freire, s/n - Cidade Universitária Recife - PE, 50740-540, Brazil}} 
+        \addr{Av. Jornalista Aníbal Fernandes, s/n - Cidade Universitária - PE, 50740-560, Brazil}} 
 \editor{-}
@@
 
-This problem is frequently referred as ``class imbalance'' problem~\cite{prati2009data} and has been encountered in multiple areas such as telecommunication managements, bioinformatics, fraud detection, and medical diagnosis.
-Imbalanced data substantially compromises the learning process since most of the standard machine learning algorithms expect balanced class distribution or an equal mis-classification cost~\cite{he2009learning}.
-Medical data are prone to such drawbacks due to the fact that the portion of diseased samples or patients is far lower than healthy cases.
-Furthermore, the detection and classification of minority malignant cases are highly essential so that the sensitivity of developed algorithms need to be maximized.
-Consequently, the problem of imbalanced data is usually addressed by employing different techniques which do not impair the topology of the data.
+Many real world datasets have many samples of some classes (majority classes),
+and only a few samples the other class (minority classes). This imbalance gives
+rise to the ``class imbalance'' problem~\cite{prati2009data} (or ``curse of imbalanced datasets'')
+which is the problem of learning a concept from the class that has a small number of samples compared
+to the other classes.
+
+The class imbalance problem has been encountered in multiple areas such as 
+telecommunication managements, bioinformatics, fraud detection, and medical diagnosis,
+and has been considered one of the top 10 problems in data mining and 
+pattern recognition~\cite{10problemsInDM:2006}. 
+Medical data, for example, are prone to suffer from class imbalance due to the fact 
+that the portion of diseased patients is far lower than healthy patients,
+and the detection and classification of minority diseased patients are highly essential
+so that they can be treated as soon as possible.
+
+Imbalanced data substantially compromises the learning process, since most of the 
+standard machine learning algorithms expect balanced class distribution or an 
+equal misclassification cost~\cite{he2009learning}. For this reason, several
+approaches have been specifically proposed to handle such datasets.
+
+In this paper, we present the \textbf{UnbalancedDataset} API, 
+\textit{a python toolbox to tackle the curse of imbalanced datasets
+in machine learning}. The following sections present the implemented
+methods, implemented design, sustainability and continuous integration details,
+and finally, the conclusion of this paper, including future functionalities
+for the UnbalancedDataset API.
+
+%This problem is frequently referred as ``class imbalance'' problem~\cite{prati2009data} and has been encountered in multiple areas such as telecommunication managements, bioinformatics, fraud detection, and medical diagnosis.
+%Imbalanced data substantially compromises the learning process since most of the standard machine learning algorithms expect balanced class distribution or an equal mis-classification cost~\cite{he2009learning}.
+%Medical data are prone to such drawbacks due to the fact that the portion of diseased samples or patients is far lower than healthy cases.
+%Furthermore, the detection and classification of minority malignant cases are highly essential so that the sensitivity of developed algorithms need to be maximized.
+%Consequently, the problem of imbalanced data is usually addressed by employing different techniques which do not impair the topology of the data.
 
@@
 
-Three strategies can be employed to overcome the problem of imbalanced dataset: (i) under-sampling, (ii) over-sampling, (iii) a combination of both, and (iv) ensemble learning.
+Three strategies can be employed to overcome the problem of imbalanced datasets: 
+(i) under-sampling, (ii) over-sampling, (iii) a combination of both, and (iv) ensemble learning.
 The following sections give an overview of the techniques used to tackle this issue.

### 2016-06-18 main.tex
go on

@@
 The state-of-the-art methods implemented can be categorized into 4 different sampling strategies: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
-The proposed toolbox depends of \emph{numpy}, \emph{scipy}, and \emph{scikit-learn}.
+The proposed toolbox only depends of \emph{numpy}, \emph{scipy}, and \emph{scikit-learn} and is distributed under MIT license.
 The implementation pattern is identical to the \emph{scikit-learn} API to offer compatibility.
 Documentation, unit tests as well as integration tests are provided to allow new developers to contribute.
-The toolbox is publicly available in GitHub \url{https://github.io} as well as the documentation \url{https://github.io}.
+The toolbox is publicly available in GitHub \url{https://github.com/fmfn/UnbalancedDataset} as well as the documentation \url{https://github.io}.
 \end{abstract}
@@
 %Consequently, the problem of imbalanced data is usually addressed by employing different techniques which do not impair the topology of the data.
+
+\section{Project management}
+
+\begin{description}
+  \item[Quality insurance] In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1 of the toolbox.
+Furthermore, the code quality is ensured by following \texttt{PEP8} standard and each contribution is automatically check through landscape.
+  \item[Continuous integration]
+  \item[Documentation]
+\end{description}
+
+In order to be sustainable and improved over years, the current toolbox offer a detailed documentation as well as a unit and integration tests.
+A set of \emph{getting started} guide, examples, and API documentation is available.
+The API documentation is automatically generated using \emph{sphinx} and \emph{numpydoc}.
+A set of unit tests are implemented to allow back compatibility and integration of new pull-requests.
+Furthermore, automatic continuous integration is also available through Travis CI.
+Bugs can be reported through the issue tracker system provided by GitHub.
+
+\section{Implementation design}
+
+The implementation rely on \emph{numpy}, \emph{scipy}, and \emph{scikit-learn}.
+The implementation pattern is identical to the \emph{scikit-learn} API to offer compatibility.
+Each class implements 3 main functions inspired from the \emph{scikit-learn} API:
+(i) \emph{fit} computes the parameter values which are later needed to transform the data into a balanced set;
+(ii) \emph{transform} performs the sampling and return the data with the desired balancing ratio;
+and (iii) \emph{fit\_transform} is equivalent of calling the function \emph{fit} follow the function \emph{transform}.
 
@@
 
-\section{Implementation design}
+\section{Conclusion}
 
-The implementation rely on \emph{numpy}, \emph{scipy}, and \emph{scikit-learn}.
-The implementation pattern is identical to the \emph{scikit-learn} API to offer compatibility.
-Each class implements 3 main functions inspired from the \emph{scikit-learn} API:
-(i) \emph{fit} computes the parameter values which are later needed to transform the data into a balanced set;
-(ii) \emph{transform} performs the sampling and return the data with the desired balancing ratio;
-and (iii) \emph{fit\_transform} is equivalent of calling the function \emph{fit} follow the function \emph{transform}.
-
-\section{Sustainability and continuous integration}
-
-In order to be sustainable and improved over years, the current toolbox offer a detailed documentation as well as a unit and integration tests.
-A set of \emph{getting started} guide, examples, and API documentation is available.
-The API documentation is automatically generated using \emph{sphinx} and \emph{numpydoc}.
-A set of unit tests are implemented to allow back compatibility and integration of new pull-requests.
-Furthermore, automatic continuous integration is also available through Travis CI.
-Bugs can be reported through the issue tracker system provided by GitHub.
-
-\begin{description}
-  \item[Documentation]
-  \item[Unit tests]
-  \item[Integration tests]
-\end{description}
-
-\section{Conclusion}
+\acks{We would like to acknowledge support for this project
+from GitHub, Travis CI, and Gitter.}
 

### 2016-06-18 main.tex
Advance project vision

@@
 Documentation, unit tests as well as integration tests are provided to allow new developers to contribute.
-The toolbox is publicly available in GitHub \url{https://github.com/fmfn/UnbalancedDataset} as well as the documentation \url{https://github.io}.
+The toolbox is publicly available in GitHub \url{https://github.com/fmfn/UnbalancedDataset} as well as the documentation \url{http://fmfn.github.io/UnbalancedDataset/}.
 \end{abstract}
@@
   \item[Quality insurance] In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1 of the toolbox.
-Furthermore, the code quality is ensured by following \texttt{PEP8} standard and each contribution is automatically check through landscape.
-  \item[Continuous integration]
-  \item[Documentation]
+Furthermore, the code consistency is ensured by following \texttt{PEP8} standards and each new contribution is automatically check through landscape, which provides metrics related to code quality.
+  \item[Continuous integration] To allow user and developer to either use or contribute this toolbox, Travis CI is used to easily integrate new code and ensure back-compatibility.
+  \item[Community-based development] All the development is performed in a collaborative manner.
+Tools as git, GitHub, and gitter are used to ease collaborative programming, issue tracking, code integration, and ideas discussions.
+  \item[Documentation] A consistent API documentation is provided using \emph{sphinx} and \emph{numpydoc}.
+Additional installation guide, examples, and tutorial are also provided and centralized on GitHub\footnote{\url{http://fmfn.github.io/UnbalancedDataset/}}.
 \end{description}
-
-In order to be sustainable and improved over years, the current toolbox offer a detailed documentation as well as a unit and integration tests.
-A set of \emph{getting started} guide, examples, and API documentation is available.
-The API documentation is automatically generated using \emph{sphinx} and \emph{numpydoc}.
-A set of unit tests are implemented to allow back compatibility and integration of new pull-requests.
-Furthermore, automatic continuous integration is also available through Travis CI.
-Bugs can be reported through the issue tracker system provided by GitHub.
 
@@
 The implementation rely on \emph{numpy}, \emph{scipy}, and \emph{scikit-learn}.
-The implementation pattern is identical to the \emph{scikit-learn} API to offer compatibility.
 Each class implements 3 main functions inspired from the \emph{scikit-learn} API:
@@
 
-Three strategies can be employed to overcome the problem of imbalanced datasets: 
+The \textbf{UnbalancedDataset} toolbox provides four different strategies to tackle the problem of imbalanced dataset:
 (i) under-sampling, (ii) over-sampling, (iii) a combination of both, and (iv) ensemble learning.
-The following sections give an overview of the techniques used to tackle this issue.
+The following sections give an overview of the techniques implemented.
 
@@
 
-Considering the problem of imbalanced, under-sampling is performed such that the number of samples of the majority class is reduced to be equal to the number of samples of the minority class.
+Considering the problem of imbalanced, under-sampling is performed such that the number of samples of the majority class is reduced.
 The following methods are considered to perform such balancing.
@@
   \item[Random under-sampling] is performed by randomly selecting without replacement a subset of samples from the majority class such that the number of samples is then equal in both minority and majority classes.
-  \item[Tomek links] can be used to under-sample the majority class of the original dataset~\cite{tomek1976two}.
-Let define a pair of nearest neighbour samples $(x_i, x_j)$ such that their associated class label $y_i \neq y_j$.
-The pair $(x_i, x_j)$ is defined as a Tomek link if, by relaxing the class label differentiation constraint, there is no other sample $x_k$ defined as the nearest neighbour of either $x_i$ or $x_j$.
-Under-sampling is performed by removing the samples belonging to the majority class and forming a Tomek link.
-It can be noted that this under-sampling strategy does not enforce a strict balancing between the majority and the minority classes.
   \item[Cluster centroids method] refers to the use of a $k$-means to cluster the feature space such that $k$ is set to be equal to the number of samples composing the minority class.
 Hence, the centroids of these clusters define the new samples of the majority class. 
+  \item[Condensed nearest neighbours] Something here.
+  \item[Edited nearest neighbours] Something here.
+  \item[Instance hardness neigbours]
   \item[NearMiss] offers three different methods to under-sample the majority class~\cite{mani2003knn}.
@@
 In our experiment, $k$ and $m$ are fixed to 3.
+  \item[One-sided selection] Something here.
   \item[Neighbourhood cleaning rule] consists of applying two rules depending on the class of each sample~\cite{laurikkala2001improving}.
@@
 In our experiment $k$ is fixed to 3.
+  \item[Tomek links] can be used to under-sample the majority class of the original dataset~\cite{tomek1976two}.
+Let define a pair of nearest neighbour samples $(x_i, x_j)$ such that their associated class label $y_i \neq y_j$.
+The pair $(x_i, x_j)$ is defined as a Tomek link if, by relaxing the class label differentiation constraint, there is no other sample $x_k$ defined as the nearest neighbour of either $x_i$ or $x_j$.
+Under-sampling is performed by removing the samples belonging to the majority class and forming a Tomek link.
+It can be noted that this under-sampling strategy does not enforce a strict balancing between the majority and the minority classes.
+
 \end{description}
@@
 \acks{We would like to acknowledge support for this project
-from GitHub, Travis CI, and Gitter.}
+from git, GitHub, Travis CI, and Gitter.}
 

### 2016-06-19 main.tex
Going into each method

@@
 and only a few samples the other class (minority classes). This imbalance gives
-rise to the ``class imbalance'' problem~\cite{prati2009data} (or ``curse of imbalanced datasets'')
+rise to the ``class imbalance'' problem~\citep{prati2009data} (or ``curse of imbalanced datasets'')
 which is the problem of learning a concept from the class that has a small number of samples compared
@@
 and has been considered one of the top 10 problems in data mining and 
-pattern recognition~\cite{10problemsInDM:2006}. 
-Medical data, for example, are prone to suffer from class imbalance due to the fact 
-that the portion of diseased patients is far lower than healthy patients,
-and the detection and classification of minority diseased patients are highly essential
-so that they can be treated as soon as possible.
-
+pattern recognition~\citep{rastgoo2016tackling,yang200610}. 
 Imbalanced data substantially compromises the learning process, since most of the 
 standard machine learning algorithms expect balanced class distribution or an 
-equal misclassification cost~\cite{he2009learning}. For this reason, several
+equal misclassification cost~\citep{he2009learning}. For this reason, several
 approaches have been specifically proposed to handle such datasets.
+
+Such standalone methods have been implemented mainly in R language~\citep{torgo2010data,kuhn2015caret,dal2013racing}.
+Up to our knowledge, however, there is no python toolbox allowing such processing while cutting edge machine learning toolboxes are available~\citep{pedregosa2011scikit,sonnenburg2010shogun}.
 
@@
 
-%This problem is frequently referred as ``class imbalance'' problem~\cite{prati2009data} and has been encountered in multiple areas such as telecommunication managements, bioinformatics, fraud detection, and medical diagnosis.
-%Imbalanced data substantially compromises the learning process since most of the standard machine learning algorithms expect balanced class distribution or an equal mis-classification cost~\cite{he2009learning}.
+%This problem is frequently referred as ``class imbalance'' problem~\citep{prati2009data} and has been encountered in multiple areas such as telecommunication managements, bioinformatics, fraud detection, and medical diagnosis.
+%Imbalanced data substantially compromises the learning process since most of the standard machine learning algorithms expect balanced class distribution or an equal mis-classification cost~\citep{he2009learning}.
 %Medical data are prone to such drawbacks due to the fact that the portion of diseased samples or patients is far lower than healthy cases.
@@
 
-\begin{description}
-  \item[Quality insurance] In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1 of the toolbox.
+\noindent\textit{Quality insurance} In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1 of the toolbox.
 Furthermore, the code consistency is ensured by following \texttt{PEP8} standards and each new contribution is automatically check through landscape, which provides metrics related to code quality.
-  \item[Continuous integration] To allow user and developer to either use or contribute this toolbox, Travis CI is used to easily integrate new code and ensure back-compatibility.
-  \item[Community-based development] All the development is performed in a collaborative manner.
+
+\noindent\textit{Continuous integration} To allow user and developer to either use or contribute this toolbox, Travis CI is used to easily integrate new code and ensure back-compatibility.
+
+\noindent\textit{Community-based development} All the development is performed in a collaborative manner.
 Tools as git, GitHub, and gitter are used to ease collaborative programming, issue tracking, code integration, and ideas discussions.
-  \item[Documentation] A consistent API documentation is provided using \emph{sphinx} and \emph{numpydoc}.
+
+\noindent\textit{Documentation} A consistent API documentation is provided using \emph{sphinx} and \emph{numpydoc}.
 Additional installation guide, examples, and tutorial are also provided and centralized on GitHub\footnote{\url{http://fmfn.github.io/UnbalancedDataset/}}.
-\end{description}
 
@@
 
+\subsection{Notation and background}
+
+Let $\chi$ an imbalanced dataset with $\chi_{min}$ and $\chi_{maj}$ being the subset of samples belonging to the minority and majority class, respectively.
+The balancing ratio of the dataset $\chi$ is defined as:
+
+\begin{equation}
+r_{\chi} = \frac{|\chi_{maj}|}{|\chi_{min}|} \ ,
+\end{equation}
+
+\noindent where $|\cdot|$ denotes the cardinality of a set.
+
+The balancing process is equivalent to resample $\chi$ into a new dataset $\chi_{res}$ such that $r_{\chi} < r_{\chi_{res}}$.
+
 \subsection{Under-sampling}
 
-Considering the problem of imbalanced, under-sampling is performed such that the number of samples of the majority class is reduced.
+Under-sampling refers to the process of reducing the number of samples in $\chi_{maj}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$.
 The following methods are considered to perform such balancing.
 
-\begin{description}
-  \item[Random under-sampling] is performed by randomly selecting without replacement a subset of samples from the majority class such that the number of samples is then equal in both minority and majority classes.
-  \item[Cluster centroids method] refers to the use of a $k$-means to cluster the feature space such that $k$ is set to be equal to the number of samples composing the minority class.
-Hence, the centroids of these clusters define the new samples of the majority class. 
-  \item[Condensed nearest neighbours] Something here.
-  \item[Edited nearest neighbours] Something here.
-  \item[Instance hardness neigbours]
-  \item[NearMiss] offers three different methods to under-sample the majority class~\cite{mani2003knn}.
-In NearMiss-1, samples from the majority class are selected such that for each sample, the average distance to the $k$ nearest neighbour samples from the minority class is minimum.
-NearMiss-2 diverges from NearMiss-1 by considering the $k$ farthest neighbours samples from the minority class.
-In NearMiss-3, a subset $M$ containing samples from the majority class is generated by finding the $m$ nearest neighbours from each sample of the minority class.
-Then, samples from the subset $M$ are selected such that for each sample, the average distance to the $k$ nearest neighbour samples from the minority class is maximum.
-In our experiment, $k$ and $m$ are fixed to 3.
-  \item[One-sided selection] Something here.
-  \item[Neighbourhood cleaning rule] consists of applying two rules depending on the class of each sample~\cite{laurikkala2001improving}.
+\textbf{Random under-sampling} is performed by randomly selecting without replacement a subset of samples from $\chi_{maj}$ to obtain the desired balancing ratio $r_{\chi_{res}}$.
+
+\textbf{Cluster centroids method} refers to the use of a $k$-means to cluster the feature space.
+$k$ corresponds to the number of samples in $\chi_{res_{maj}}$ defined by the desired balancing ratio $r_{\chi_{res}}$.
+Note that the samples in $\chi_{res_{maj}}$ do not correspond to the original samples of $\chi_{maj}$ and are synthetically generated.
+
+\textbf{Condensed nearest neighbours} Something here.
+
+\textbf{Edited nearest neighbours} Something here.
+
+\textbf{Instance hardness threshold}
+
+\textbf{NearMiss} offers three different methods to under-sample the majority class~\citep{mani2003knn}.
+In NearMiss-1, samples $\chi_{maj}$ are selected such that for each sample, the average distance to the $k$ nearest neighbour samples from $\chi_{min}$ is minimum.
+NearMiss-2 diverges from NearMiss-1 by considering the $k$ farthest neighbours samples from $\chi_{min}$.
+In NearMiss-3, a subset $M$ containing samples from the $\chi_{maj}$ is generated by finding the $m$ nearest neighbours from each sample of $\chi_{min}$.
+Then, samples from the subset $M$ are selected such that for each sample, the average distance to the $k$ nearest neighbour samples from $\chi_{min}$ is maximum.
+
+\textbf{One-sided selection} Something here.
+
+\textbf{Neighbourhood cleaning rule} consists of applying two rules depending on the class of each sample~\citep{laurikkala2001improving}.
 Let define $x_i$ as a sample of the dataset with its associated class label $y_i$.
 Let define $y_m$ as the class of the majority vote of the $k$ nearest neighbours of the sample $x_i$.
-If $y_i$ corresponds to the majority class and $y_i \neq y_m$, $x_i$ is rejected from the final subset.
-If $y_i$ corresponds to the minority class and and $y_i \neq y_m$, then the $k$ nearest neighbours are rejected from the final subset.
-In our experiment $k$ is fixed to 3.
-  \item[Tomek links] can be used to under-sample the majority class of the original dataset~\cite{tomek1976two}.
+If $y_i$ corresponds to $\chi_{maj}$ and $y_i \neq y_m$, $x_i$ is rejected from the final subset.
+If $y_i$ corresponds to $\chi_{min}$ class and and $y_i \neq y_m$, then the $k$ nearest neighbours are rejected from the final subset.
+
+\textbf{Tomek links} can be used to under-sample $\chi_{maj}$~\citep{tomek1976two}.
 Let define a pair of nearest neighbour samples $(x_i, x_j)$ such that their associated class label $y_i \neq y_j$.
-The pair $(x_i, x_j)$ is defined as a Tomek link if, by relaxing the class label differentiation constraint, there is no other sample $x_k$ defined as the nearest neighbour of either $x_i$ or $x_j$.
-Under-sampling is performed by removing the samples belonging to the majority class and forming a Tomek link.
-It can be noted that this under-sampling strategy does not enforce a strict balancing between the majority and the minority classes.
-
-\end{description}
+The pair $(x_i, x_j)$ is defined as a Tomek link if, by relaxing the class label differentiation constraint; there is no other sample $x_k$ defined as the nearest neighbour of either $x_i$ or $x_j$.
+Under-sampling is performed by removing the samples belonging to $\chi_{maj}$ and forming a Tomek link.
 
@@
 Two different methods are considered.
-\begin{description}
-\item[Random over-sampling] is performed by randomly replicating the samples of the minority class such that the number of samples is equal in both minority and majority classes.
-\end{description}
-\begin{description}
-\item[SMOTE] is a method to generate synthetic samples in the feature space~\cite{chawla2002smote}.
+
+\textbf{Random over-sampling} is performed by randomly replicating the samples of the minority class such that the number of samples is equal in both minority and majority classes.
+
+\textbf{SMOTE} is a method to generate synthetic samples in the feature space~\citep{chawla2002smote}.
 Let define $x_i$ as a sample belonging to the minority class.
@@
 Three other variants of this algorithm exist: (i) SMOTE borderline 1, (ii) SMOTE borderline 2, and (iii) SMOTE SVM.
-\end{description}
 
@@
 
-\begin{description}
-  \item[SMOTE + Tomek links] are combined to clean the samples created using SMOTE~\cite{batista2003balancing}.
-SMOTE over-sampling can lead to over-fitting which can be avoided by removing the Tomek links from both majority and minority classes~\cite{prati2009data}.
-  \item[SMOTE + edited nearest neighbours] are combined for the same aforementioned reason~\cite{batista2004study}.
-\end{description}
+\textbf{SMOTE + Tomek links} are combined to clean the samples created using SMOTE~\citep{batista2003balancing}.
+SMOTE over-sampling can lead to over-fitting which can be avoided by removing the Tomek links from both majority and minority classes~\citep{prati2009data}.
+\textbf{SMOTE + edited nearest neighbours} are combined for the same aforementioned reason~\citep{batista2004study}.
 
@@
 
-\begin{description}
-  \item[Balance cascade]
-  \item[Easy ensemble]
-\end{description}
+\textbf{Balance cascade} Something here
+
+\textbf{Easy ensemble} Something here
 

### 2016-06-21 main.tex
Advance the writting

@@
 \begin{abstract}
-\emph{UnbalancedDataset} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
+\texttt{UnbalancedDataset} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
 The state-of-the-art methods implemented can be categorized into 4 different sampling strategies: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
-The proposed toolbox only depends of \emph{numpy}, \emph{scipy}, and \emph{scikit-learn} and is distributed under MIT license.
-The implementation pattern is identical to the \emph{scikit-learn} API to offer compatibility.
-Documentation, unit tests as well as integration tests are provided to allow new developers to contribute.
-The toolbox is publicly available in GitHub \url{https://github.com/fmfn/UnbalancedDataset} as well as the documentation \url{http://fmfn.github.io/UnbalancedDataset/}.
+The proposed toolbox only depends of \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
+Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
+The toolbox is publicly available in GitHub \url{https://github.com/fmfn/UnbalancedDataset}.
 \end{abstract}
@@
 
-Many real world datasets have many samples of some classes (majority classes),
-and only a few samples the other class (minority classes). This imbalance gives
-rise to the ``class imbalance'' problem~\citep{prati2009data} (or ``curse of imbalanced datasets'')
+Real world datasets commonly show the particularity to have the number of samples of a class under-represented compared to other classes.
+This imbalance gives rise to the ``class imbalance'' problem~\citep{prati2009data} (or ``curse of imbalanced datasets'')
 which is the problem of learning a concept from the class that has a small number of samples compared
@@
 approaches have been specifically proposed to handle such datasets.
-
 Such standalone methods have been implemented mainly in R language~\citep{torgo2010data,kuhn2015caret,dal2013racing}.
@@
 
-In this paper, we present the \textbf{UnbalancedDataset} API, 
+In this paper, we present the \texttt{UnbalancedDataset} API, 
 \textit{a python toolbox to tackle the curse of imbalanced datasets
@@
 and finally, the conclusion of this paper, including future functionalities
-for the UnbalancedDataset API.
-
-%This problem is frequently referred as ``class imbalance'' problem~\citep{prati2009data} and has been encountered in multiple areas such as telecommunication managements, bioinformatics, fraud detection, and medical diagnosis.
-%Imbalanced data substantially compromises the learning process since most of the standard machine learning algorithms expect balanced class distribution or an equal mis-classification cost~\citep{he2009learning}.
-%Medical data are prone to such drawbacks due to the fact that the portion of diseased samples or patients is far lower than healthy cases.
-%Furthermore, the detection and classification of minority malignant cases are highly essential so that the sensitivity of developed algorithms need to be maximized.
-%Consequently, the problem of imbalanced data is usually addressed by employing different techniques which do not impair the topology of the data.
+for the \texttt{UnbalancedDataset} API.
 
@@
 
-\noindent\textit{Documentation} A consistent API documentation is provided using \emph{sphinx} and \emph{numpydoc}.
+\noindent\textit{Documentation} A consistent API documentation is provided using \texttt{sphinx} and \texttt{numpydoc}.
 Additional installation guide, examples, and tutorial are also provided and centralized on GitHub\footnote{\url{http://fmfn.github.io/UnbalancedDataset/}}.
@@
 
-The implementation rely on \emph{numpy}, \emph{scipy}, and \emph{scikit-learn}.
-Each class implements 3 main functions inspired from the \emph{scikit-learn} API:
-(i) \emph{fit} computes the parameter values which are later needed to transform the data into a balanced set;
-(ii) \emph{transform} performs the sampling and return the data with the desired balancing ratio;
-and (iii) \emph{fit\_transform} is equivalent of calling the function \emph{fit} follow the function \emph{transform}.
+The implementation rely on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn}.
+Each class implements 3 main functions inspired from the \texttt{scikit-learn} API:
+(i) \texttt{fit} computes the parameter values which are later needed to transform the data into a balanced set;
+(ii) \texttt{transform} performs the sampling and return the data with the desired balancing ratio;
+and (iii) \texttt{fit\_transform} is equivalent of calling the function \texttt{fit} follow the function \texttt{transform}.
 
@@
 
-The \textbf{UnbalancedDataset} toolbox provides four different strategies to tackle the problem of imbalanced dataset:
+The \texttt{UnbalancedDataset} toolbox provides four different strategies to tackle the problem of imbalanced dataset:
 (i) under-sampling, (ii) over-sampling, (iii) a combination of both, and (iv) ensemble learning.
@@
 
-In the contrary, the data balancing can be performed by over-sampling in which the new samples belonging to the minority class are generated aiming at equalizing the number of samples in both classes.
-Two different methods are considered.
+In the contrary of under-sampling, data balancing can be performed by over-sampling in which new samples are generated in $\chi_{min}$ to reach the balancing ratio $r_{\chi_{res}}$.
+The following methods are currently available.
 
-\textbf{Random over-sampling} is performed by randomly replicating the samples of the minority class such that the number of samples is equal in both minority and majority classes.
+\textbf{Random over-sampling} is performed by randomly replicating the samples of $\chi_{min}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$.
 
@@
 SMOTE over-sampling can lead to over-fitting which can be avoided by removing the Tomek links from both majority and minority classes~\citep{prati2009data}.
+
 \textbf{SMOTE + edited nearest neighbours} are combined for the same aforementioned reason~\citep{batista2004study}.

### 2016-06-21 main.tex
Finish the first draft

@@
 \usepackage{jmlr2e}
+\usepackage{listings}
+\usepackage{color}
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},   
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\tiny\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\footnotesize,
+    breakatwhitespace=false,         
+    breaklines=true,                 
+    captionpos=b,                    
+    keepspaces=true,                 
+    numbers=left,                    
+    numbersep=5pt,                  
+    showspaces=false,                
+    showstringspaces=false,
+    showtabs=false,                  
+    tabsize=2
+}
+
+\lstset{style=mystyle}
 
@@
 \textit{a python toolbox to tackle the curse of imbalanced datasets
-in machine learning}. The following sections present the implemented
-methods, implemented design, sustainability and continuous integration details,
+in machine learning}. The following sections present the project vision, a snapshot of the API, an overview of the implemented methods,
 and finally, the conclusion of this paper, including future functionalities
@@
 \noindent\textit{Documentation} A consistent API documentation is provided using \texttt{sphinx} and \texttt{numpydoc}.
-Additional installation guide, examples, and tutorial are also provided and centralized on GitHub\footnote{\url{http://fmfn.github.io/UnbalancedDataset/}}.
+Additional installation guide and examples are also provided and centralized on GitHub\footnote{\url{http://fmfn.github.io/UnbalancedDataset/}}.
+
+\noindent\textit{Project relevance} At the edition time, the repository is visited no less than $2,000$ per week, attracting about $300$ unique visitors per week.
 
 \section{Implementation design}
+
+\begin{lstlisting}[language=Python, caption=Code snippet to over-sample a dataset using SMOTE.]
+from sklearn.datasets import make_classification
+from sklearn.decomposition import PCA
+
+from unbalanced_dataset.over_sampling import SMOTE
+
+# Generate the dataset
+X, y = make_classification(n_classes=2, class_sep=2, weights=[0.1, 0.9],
+                           n_informative=3, n_redundant=1, flip_y=0,
+                           n_features=20, n_clusters_per_class=1,
+                           n_samples=5000, random_state=10)
+
+# Apply the SMOTE over-sampling
+sm = SMOTE(ratio='auto', kind='regular')
+X_resampled, y_resampled = sm.fit_transform(X, y)
+\end{lstlisting}
 
@@
 
-\noindent where $|\cdot|$ denotes the cardinality of a set.
-
-The balancing process is equivalent to resample $\chi$ into a new dataset $\chi_{res}$ such that $r_{\chi} < r_{\chi_{res}}$.
+\noindent where $|\cdot|$ denotes the cardinality of a set. The balancing process is equivalent to resample $\chi$ into a new dataset $\chi_{res}$ such that $r_{\chi} < r_{\chi_{res}}$.
 
@@
 
-Under-sampling refers to the process of reducing the number of samples in $\chi_{maj}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$.
-The following methods are considered to perform such balancing.
+Under-sampling refers to the process of reducing the number of samples in $\chi_{maj}$.
+The implemented methods can be categorized into 2 groups: (i) fixed under-sampling, (ii) cleaning under-sampling.
 
-\textbf{Random under-sampling} is performed by randomly selecting without replacement a subset of samples from $\chi_{maj}$ to obtain the desired balancing ratio $r_{\chi_{res}}$.
+\emph{Fixed under-sampling} refer to the methods which perform under-sampling to obtain the appropriate balancing ratio $r_{\chi_{res}}$.
+The implemented methods perform the under-sampling based on different criteria: (i) random selection, (ii) clustering, (iii) nearest neighbours rule (i.e., \textit{NearMiss}~\citep{mani2003knn}), and (iv) classification accuracy (i.e., \texttt{instance hardness threshold}~\citep{smith2014instance}).
 
-\textbf{Cluster centroids method} refers to the use of a $k$-means to cluster the feature space.
-$k$ corresponds to the number of samples in $\chi_{res_{maj}}$ defined by the desired balancing ratio $r_{\chi_{res}}$.
-Note that the samples in $\chi_{res_{maj}}$ do not correspond to the original samples of $\chi_{maj}$ and are synthetically generated.
+In the contrary to the previous methods, \emph{cleaning under-sampling} do not allow to reach specifically the balancing ratio $r_{\chi_{res}}$, but rather clean the feature space based on some empirical criteria.
+These criteria are derived from the nearest neighbours rule, namely: (i) \texttt{condensed nearest neighbours}~\citep{hart1968condensed}, (ii) \texttt{edited nearest neighbours}~\citep{wilson1972asymptotic}, (iii) \texttt{one-sided selection}~\citep{kubat1997addressing}, (iv) \texttt{neighbourhood cleaning rule}~\citep{laurikkala2001improving}, and (v) \texttt{Tomek links}~\citep{tomek1976two}.
 
-\textbf{Condensed nearest neighbours} Something here.
+% Under-sampling refers to the process of reducing the number of samples in $\chi_{maj}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$.
+% The following methods are considered to perform such balancing.
 
-\textbf{Edited nearest neighbours} Something here.
+% \texttt{Random under-sampling} is performed by randomly selecting without replacement a subset of samples from $\chi_{maj}$ to obtain the desired balancing ratio $r_{\chi_{res}}$.
 
-\textbf{Instance hardness threshold}
+% \texttt{Cluster centroids method} refers to the use of a $k$-means to cluster the feature space.
+% $k$ corresponds to the number of samples in $\chi_{res_{maj}}$ defined by the desired balancing ratio $r_{\chi_{res}}$.
+% Note that the samples in $\chi_{res_{maj}}$ do not correspond to the original samples of $\chi_{maj}$ and are synthetically generated.
 
-\textbf{NearMiss} offers three different methods to under-sample the majority class~\citep{mani2003knn}.
-In NearMiss-1, samples $\chi_{maj}$ are selected such that for each sample, the average distance to the $k$ nearest neighbour samples from $\chi_{min}$ is minimum.
-NearMiss-2 diverges from NearMiss-1 by considering the $k$ farthest neighbours samples from $\chi_{min}$.
-In NearMiss-3, a subset $M$ containing samples from the $\chi_{maj}$ is generated by finding the $m$ nearest neighbours from each sample of $\chi_{min}$.
-Then, samples from the subset $M$ are selected such that for each sample, the average distance to the $k$ nearest neighbour samples from $\chi_{min}$ is maximum.
+% \texttt{Condensed nearest neighbours} \citep{hart1968condensed}
 
-\textbf{One-sided selection} Something here.
+% \texttt{Edited nearest neighbours} \citep{wilson1972asymptotic}
 
-\textbf{Neighbourhood cleaning rule} consists of applying two rules depending on the class of each sample~\citep{laurikkala2001improving}.
-Let define $x_i$ as a sample of the dataset with its associated class label $y_i$.
-Let define $y_m$ as the class of the majority vote of the $k$ nearest neighbours of the sample $x_i$.
-If $y_i$ corresponds to $\chi_{maj}$ and $y_i \neq y_m$, $x_i$ is rejected from the final subset.
-If $y_i$ corresponds to $\chi_{min}$ class and and $y_i \neq y_m$, then the $k$ nearest neighbours are rejected from the final subset.
+% \texttt{Instance hardness threshold} \citep{smith2014instance}
 
-\textbf{Tomek links} can be used to under-sample $\chi_{maj}$~\citep{tomek1976two}.
-Let define a pair of nearest neighbour samples $(x_i, x_j)$ such that their associated class label $y_i \neq y_j$.
-The pair $(x_i, x_j)$ is defined as a Tomek link if, by relaxing the class label differentiation constraint; there is no other sample $x_k$ defined as the nearest neighbour of either $x_i$ or $x_j$.
-Under-sampling is performed by removing the samples belonging to $\chi_{maj}$ and forming a Tomek link.
+% \texttt{NearMiss} offers three different methods to under-sample the majority class~\citep{mani2003knn}.
+% In NearMiss-1, samples $\chi_{maj}$ are selected such that for each sample, the average distance to the $k$ nearest neighbour samples from $\chi_{min}$ is minimum.
+% NearMiss-2 diverges from NearMiss-1 by considering the $k$ farthest neighbours samples from $\chi_{min}$.
+% In NearMiss-3, a subset $M$ containing samples from the $\chi_{maj}$ is generated by finding the $m$ nearest neighbours from each sample of $\chi_{min}$.
+% Then, samples from the subset $M$ are selected such that for each sample, the average distance to the $k$ nearest neighbour samples from $\chi_{min}$ is maximum.
+
+% \texttt{One-sided selection} \citep{kubat1997addressing}
+
+% \texttt{Neighbourhood cleaning rule} consists of applying two rules depending on the class of each sample~\citep{laurikkala2001improving}.
+% Let define $x_i$ as a sample of the dataset with its associated class label $y_i$.
+% Let define $y_m$ as the class of the majority vote of the $k$ nearest neighbours of the sample $x_i$.
+% If $y_i$ corresponds to $\chi_{maj}$ and $y_i \neq y_m$, $x_i$ is rejected from the final subset.
+% If $y_i$ corresponds to $\chi_{min}$ class and and $y_i \neq y_m$, then the $k$ nearest neighbours are rejected from the final subset.
+
+% \texttt{Tomek links} can be used to under-sample $\chi_{maj}$~\citep{tomek1976two}.
+% Let define a pair of nearest neighbour samples $(x_i, x_j)$ such that their associated class label $y_i \neq y_j$.
+% The pair $(x_i, x_j)$ is defined as a Tomek link if, by relaxing the class label differentiation constraint; there is no other sample $x_k$ defined as the nearest neighbour of either $x_i$ or $x_j$.
+% Under-sampling is performed by removing the samples belonging to $\chi_{maj}$ and forming a Tomek link.
 
@@
 
-In the contrary of under-sampling, data balancing can be performed by over-sampling in which new samples are generated in $\chi_{min}$ to reach the balancing ratio $r_{\chi_{res}}$.
-The following methods are currently available.
+In the contrary of under-sampling, data balancing can be performed by over-sampling such that new samples are generated in $\chi_{min}$ to reach the balancing ratio $r_{\chi_{res}}$.
+Two methods are currently available: (i) \texttt{Random over-sampling} is performed by randomly replicating the samples of $\chi_{min}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$ and \texttt{SMOTE} which randomly generate new samples between tuple of nearest neighbours of $\chi_{min}$~\citep{chawla2002smote}.
+Different variants of this algorithm have been proposed: \texttt{SMOTE borderline 1 \& 2}~\citep{han2005borderline} and \texttt{SMOTE SVM}~\citep{nguyen2011borderline}
 
-\textbf{Random over-sampling} is performed by randomly replicating the samples of $\chi_{min}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$.
-
-\textbf{SMOTE} is a method to generate synthetic samples in the feature space~\citep{chawla2002smote}.
-Let define $x_i$ as a sample belonging to the minority class.
-Let define $x_{nn}$ as a randomly selected sample from the $k$ nearest neighbours of $x_i$, with $k$ set to 3.
-Therefore, a new sample $x_j$ is generated such that $x_j = x_i + \sigma \left( x_{nn} - x_i \right)$, where $\sigma$ is a random number in the interval $\left[0,1\right]$.
-Three other variants of this algorithm exist: (i) SMOTE borderline 1, (ii) SMOTE borderline 2, and (iii) SMOTE SVM.
+% \texttt{SMOTE} is a method to generate synthetic samples in the feature space~\citep{chawla2002smote}.
+% Let define $x_i$ as a sample belonging to the minority class.
+% Let define $x_{nn}$ as a randomly selected sample from the $k$ nearest neighbours of $x_i$, with $k$ set to 3.
+% Therefore, a new sample $x_j$ is generated such that $x_j = x_i + \sigma \left( x_{nn} - x_i \right)$, where $\sigma$ is a random number in the interval $\left[0,1\right]$.
+% Some variants of this algorithm have been proposed: \texttt{SMOTE borderline 1 \& 2}~\citep{han2005borderline} and \texttt{SMOTE SVM}~\citep{nguyen2011borderline}.
 
@@
 
-Subsequently, over-sampling methods can be combined with under-sampling methods to clean the subset created.
-In that regard, two different combinations are tested.
-
-\textbf{SMOTE + Tomek links} are combined to clean the samples created using SMOTE~\citep{batista2003balancing}.
-SMOTE over-sampling can lead to over-fitting which can be avoided by removing the Tomek links from both majority and minority classes~\citep{prati2009data}.
-
-\textbf{SMOTE + edited nearest neighbours} are combined for the same aforementioned reason~\citep{batista2004study}.
+\texttt{SMOTE} over-sampling can lead to over-fitting which can be avoided by applying cleaning under-sampling methods~\citep{prati2009data}.
+In that regard, \cite{batista2003balancing} combined \texttt{SMOTE} either with \texttt{Tomek links} or \texttt{edited nearest neighbours}.
 
@@
 
-Under-sampling methods implies that samples of the majority class will be lost during the balancing procedure.
-Ensemble methods can offer an alternative to use most of the samples.
-In fact, an ensemble of balanced set will be created and used to later train any classifier.
-Two methods are available to build such ensemble.
-
-\textbf{Balance cascade} Something here
-
-\textbf{Easy ensemble} Something here
+Under-sampling methods implies that samples of the majority class are lost during the balancing procedure.
+Ensemble methods offer an alternative to use most of the samples.
+In fact, an ensemble of balanced sets is created and used to later train any classifier.
+Two methods are available to build such ensemble proposed by~\cite{liu2009exploratory}: \texttt{EasyEnsemble} and \texttt{BalanceCascade}.
+The former is based on iteratively applying the \texttt{random under-sampling} method to build several sets, each of them with a desired balancing ratio $r_{\chi_{res}}$.
+The latter differs from the former such that a classifier is used at each iteration to determine the class of the randomly selected samples.
+Misclassified samples will be kept and propagated in the next subset.
 
@@
 
-\acks{We would like to acknowledge support for this project
-from git, GitHub, Travis CI, and Gitter.}
+In this paper, we shortly presented the foundations of the \texttt{UnbalancedDataset} toolbox vision and API.
+As avenues for future work, the toolbox is intended to be fully part of a \texttt{scikit-learn-contrib} repository.
+
+% \acks{We would like to acknowledge support for this project
+% from git, GitHub, Travis CI, and Gitter.}
 

### 2016-06-21 main.tex
Correct some mistakes

@@
 \texttt{UnbalancedDataset} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
-The state-of-the-art methods implemented can be categorized into 4 different sampling strategies: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
+The implemented state-of-the-art methods can be categorized into 4 groups: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
 The proposed toolbox only depends of \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
@@
 
-Real world datasets commonly show the particularity to have the number of samples of a class under-represented compared to other classes.
+Real world datasets commonly show the particularity to have a number of samples of a given class under-represented compared to other classes.
 This imbalance gives rise to the ``class imbalance'' problem~\citep{prati2009data} (or ``curse of imbalanced datasets'')
-which is the problem of learning a concept from the class that has a small number of samples compared
-to the other classes.
+which is the problem of learning a concept from the class that has a small number of samples.
 
@@
 and has been considered one of the top 10 problems in data mining and 
-pattern recognition~\citep{rastgoo2016tackling,yang200610}. 
+pattern recognition~\citep{yang200610,rastgoo2016tackling}. 
 Imbalanced data substantially compromises the learning process, since most of the 
@@
 
-\noindent\textit{Continuous integration} To allow user and developer to either use or contribute this toolbox, Travis CI is used to easily integrate new code and ensure back-compatibility.
+\noindent\textit{Continuous integration} To allow user and developer to either use or contribute to this toolbox, Travis CI is used to easily integrate new code and ensure back-compatibility.
 
@@
 (ii) \texttt{transform} performs the sampling and return the data with the desired balancing ratio;
-and (iii) \texttt{fit\_transform} is equivalent of calling the function \texttt{fit} follow the function \texttt{transform}.
+and (iii) \texttt{fit\_transform} is equivalent of calling the function \texttt{fit} followed by the function \texttt{transform}.
 
@@
 \begin{equation}
-r_{\chi} = \frac{|\chi_{maj}|}{|\chi_{min}|} \ ,
+r_{\chi} = \frac{|\chi_{min}|}{|\chi_{majB}|} \ ,
 \end{equation}
 
-\noindent where $|\cdot|$ denotes the cardinality of a set. The balancing process is equivalent to resample $\chi$ into a new dataset $\chi_{res}$ such that $r_{\chi} < r_{\chi_{res}}$.
+\noindent where $|\cdot|$ denotes the cardinality of a set. The balancing process is equivalent to resample $\chi$ into a new dataset $\chi_{res}$ such that $r_{\chi} > r_{\chi_{res}}$.
 

### 2016-06-21 main.tex
Correct some other mistakes

@@
 Under-sampling refers to the process of reducing the number of samples in $\chi_{maj}$.
-The implemented methods can be categorized into 2 groups: (i) fixed under-sampling, (ii) cleaning under-sampling.
+The implemented methods can be categorized into 2 groups: (i) fixed under-sampling and (ii) cleaning under-sampling.
 
 \emph{Fixed under-sampling} refer to the methods which perform under-sampling to obtain the appropriate balancing ratio $r_{\chi_{res}}$.
-The implemented methods perform the under-sampling based on different criteria: (i) random selection, (ii) clustering, (iii) nearest neighbours rule (i.e., \textit{NearMiss}~\citep{mani2003knn}), and (iv) classification accuracy (i.e., \texttt{instance hardness threshold}~\citep{smith2014instance}).
+The implemented methods perform the under-sampling based on different criteria such as: (i) random selection, (ii) clustering, (iii) nearest neighbours rule (i.e., \texttt{NearMiss}~\citep{mani2003knn}), and (iv) classification accuracy (i.e., \texttt{instance hardness threshold}~\citep{smith2014instance}).
 
@@
 The latter differs from the former such that a classifier is used at each iteration to determine the class of the randomly selected samples.
-Misclassified samples will be kept and propagated in the next subset.
+Misclassified samples are kept and propagated in the next subset.
 

### 2016-06-24 main.tex
Change in previoson of scikit-learn-contrib

@@
 \begin{abstract}
-\texttt{UnbalancedDataset} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
+\texttt{imbalanced-learn} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
 The implemented state-of-the-art methods can be categorized into 4 groups: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
 The proposed toolbox only depends of \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
+Furthermore, it is fully compatible with \texttt{scikit-learn} and is part of the \texttt{scikit-learn-contrib} supported project.
 Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
@@
 
-In this paper, we present the \texttt{UnbalancedDataset} API, 
+In this paper, we present the \texttt{imbalanced-learn} API, 
 \textit{a python toolbox to tackle the curse of imbalanced datasets
@@
 and finally, the conclusion of this paper, including future functionalities
-for the \texttt{UnbalancedDataset} API.
+for the \texttt{imbalanced-learn} API.
 
@@
 \noindent\textit{Project relevance} At the edition time, the repository is visited no less than $2,000$ per week, attracting about $300$ unique visitors per week.
+Additionally, the toolbox is supported by \texttt{scikit-learn} through the \texttt{scikit-learn-contrib} projects.
 
@@
 sm = SMOTE(ratio='auto', kind='regular')
-X_resampled, y_resampled = sm.fit_transform(X, y)
+X_resampled, y_resampled = sm.fit_sample(X, y)
 \end{lstlisting}
@@
 (i) \texttt{fit} computes the parameter values which are later needed to transform the data into a balanced set;
-(ii) \texttt{transform} performs the sampling and return the data with the desired balancing ratio;
-and (iii) \texttt{fit\_transform} is equivalent of calling the function \texttt{fit} followed by the function \texttt{transform}.
+(ii) \texttt{sample} performs the sampling and return the data with the desired balancing ratio;
+and (iii) \texttt{fit\_sample} is equivalent of calling the function \texttt{fit} followed by the function \texttt{transform}.
 
@@
 
-The \texttt{UnbalancedDataset} toolbox provides four different strategies to tackle the problem of imbalanced dataset:
+The \texttt{imbalanced-learn} toolbox provides four different strategies to tackle the problem of imbalanced dataset:
 (i) under-sampling, (ii) over-sampling, (iii) a combination of both, and (iv) ensemble learning.
@@
 
-In this paper, we shortly presented the foundations of the \texttt{UnbalancedDataset} toolbox vision and API.
-As avenues for future work, the toolbox is intended to be fully part of a \texttt{scikit-learn-contrib} repository.
+In this paper, we shortly presented the foundations of the \texttt{imbalanced-learn} toolbox vision and API.
 

### 2016-06-26 main.tex
add pipeline

@@
 (ii) \texttt{sample} performs the sampling and return the data with the desired balancing ratio;
-and (iii) \texttt{fit\_sample} is equivalent of calling the function \texttt{fit} followed by the function \texttt{transform}.
+and (iii) \texttt{fit\_sample} is equivalent of calling the function \texttt{fit} followed by the function \texttt{sample}.
+A class \texttt{Pipeline} is inherited from \texttt{scikit-learn} toolbox to automatically combine \texttt{sampler}, \texttt{transformers}, and \texttt{estimators}.
 

### 2016-06-26 main.tex
Proofreading, conforming new API and edit suggestions

--- 2016-06-21 main.tex
@@
 % Heading arguments are {volume}{year}{pages}{submitted}{published}{author-full-names}
-\jmlrheading{7}{2016}{1-5}{7/16}{-}{Guillaume Lema\^itre, Fernando Nogueira, and Dayvid V. R. Oliveira}
+\jmlrheading{7}{2016}{1-5}{7/16}{-}{Guillaume Lema\^itre, Fernando Nogueira, Dayvid V. R. Oliveira and Christos K. Aridas}
 
 % Short headings should be running head and authors last names
-\ShortHeadings{A python toolbox to tackle the curse of imbalanced datasets in machine learning}{Lema\^itre, Nogueira, and Victor}
+\ShortHeadings{A python toolbox to tackle the curse of imbalanced datasets in machine learning}{Lema\^itre, Nogueira, Victor, and Aridas}
 \firstpageno{1}
@@
         %\addr{Av. Prof. Luiz Freire, s/n - Cidade Universitária Recife - PE, 50740-540, Brazil}} 
-        \addr{Av. Jornalista Aníbal Fernandes, s/n - Cidade Universitária - PE, 50740-560, Brazil}} 
+        \addr{Av. Jornalista Aníbal Fernandes, s/n - Cidade Universitária - PE, 50740-560, Brazil}
+        \AND
+        Christos K. Aridas \email char@upatras.gr \\ 
+        \addr{Department of Mathematics, University of Patras} \\ 
+        \addr{University Campus, GR-26110 Patras, Greece}} 
 \editor{-}
@@
 The implemented state-of-the-art methods can be categorized into 4 groups: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
-The proposed toolbox only depends of \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
+The proposed toolbox only depends on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
 Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
@@
 \noindent\textit{Quality insurance} In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1 of the toolbox.
-Furthermore, the code consistency is ensured by following \texttt{PEP8} standards and each new contribution is automatically check through landscape, which provides metrics related to code quality.
+Furthermore, the code consistency is ensured by following \texttt{PEP8} standards and each new contribution is automatically checked through landscape, which provides metrics related to code quality.
 
@@
 \noindent\textit{Community-based development} All the development is performed in a collaborative manner.
-Tools as git, GitHub, and gitter are used to ease collaborative programming, issue tracking, code integration, and ideas discussions.
+Tools such as git, GitHub, and gitter are used to ease collaborative programming, issue tracking, code integration, and idea discussions.
 
 \noindent\textit{Documentation} A consistent API documentation is provided using \texttt{sphinx} and \texttt{numpydoc}.
-Additional installation guide and examples are also provided and centralized on GitHub\footnote{\url{http://fmfn.github.io/UnbalancedDataset/}}.
+An additional installation guide and examples are also provided and centralized on GitHub\footnote{\url{http://fmfn.github.io/UnbalancedDataset/}}.
 
@@
 sm = SMOTE(ratio='auto', kind='regular')
-X_resampled, y_resampled = sm.fit_transform(X, y)
+X_resampled, y_resampled = sm.fit_sample(X, y)
 \end{lstlisting}
 
-The implementation rely on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn}.
-Each class implements 3 main functions inspired from the \texttt{scikit-learn} API:
-(i) \texttt{fit} computes the parameter values which are later needed to transform the data into a balanced set;
-(ii) \texttt{transform} performs the sampling and return the data with the desired balancing ratio;
-and (iii) \texttt{fit\_transform} is equivalent of calling the function \texttt{fit} followed by the function \texttt{transform}.
+The implementation relies on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn}.
+Each class implements 3 main methods inspired from the \texttt{scikit-learn} API:
+(i) \texttt{fit} computes the parameter values which are later needed to resample the data into a balanced set;
+(ii) \texttt{sample} performs the sampling and returns the data with the desired balancing ratio;
+and (iii) \texttt{fit\_sample} is equivalent to calling the method \texttt{fit} followed by the method \texttt{sample}.
 
@@
 (i) under-sampling, (ii) over-sampling, (iii) a combination of both, and (iv) ensemble learning.
-The following sections give an overview of the techniques implemented.
+The following subsections give an overview of the techniques implemented.
 
@@
 
-In the contrary of under-sampling, data balancing can be performed by over-sampling such that new samples are generated in $\chi_{min}$ to reach the balancing ratio $r_{\chi_{res}}$.
+In the contrary to under-sampling, data balancing can be performed by over-sampling such that new samples are generated in $\chi_{min}$ to reach the balancing ratio $r_{\chi_{res}}$.
 Two methods are currently available: (i) \texttt{Random over-sampling} is performed by randomly replicating the samples of $\chi_{min}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$ and \texttt{SMOTE} which randomly generate new samples between tuple of nearest neighbours of $\chi_{min}$~\citep{chawla2002smote}.
@@
 
-Under-sampling methods implies that samples of the majority class are lost during the balancing procedure.
+Under-sampling methods imply that samples of the majority class are lost during the balancing procedure.
 Ensemble methods offer an alternative to use most of the samples.
@@
 The former is based on iteratively applying the \texttt{random under-sampling} method to build several sets, each of them with a desired balancing ratio $r_{\chi_{res}}$.
-The latter differs from the former such that a classifier is used at each iteration to determine the class of the randomly selected samples.
+The latter differs from the former in that a classifier is used at each iteration to determine the class of the randomly selected samples.
 Misclassified samples are kept and propagated in the next subset.

### 2016-06-26 main.tex

@@
 % Short headings should be running head and authors last names
-\ShortHeadings{A python toolbox to tackle the curse of imbalanced datasets in machine learning}{Lema\^itre, Nogueira, Victor, and Aridas}
+\ShortHeadings{A python toolbox to tackle the curse of imbalanced datasets in machine learning}{Lema\^itre, Nogueira, Oliveira, and Aridas}
 \firstpageno{1}
@@
 \begin{abstract}
-\texttt{UnbalancedDataset} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
+\texttt{imbalanced-learn} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
 The implemented state-of-the-art methods can be categorized into 4 groups: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
 The proposed toolbox only depends on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
+Furthermore, it is fully compatible with \texttt{scikit-learn} and is part of the \texttt{scikit-learn-contrib} supported project.
 Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
@@
 and (iii) \texttt{fit\_sample} is equivalent to calling the method \texttt{fit} followed by the method \texttt{sample}.
+A class \texttt{Pipeline} is inherited from \texttt{scikit-learn} toolbox to automatically combine \texttt{sampler}, \texttt{transformers}, and \texttt{estimators}.
 

### 2016-06-26 main.tex
Put on hold scikit learn contrib

@@
 The proposed toolbox only depends on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
-Furthermore, it is fully compatible with \texttt{scikit-learn} and is part of the \texttt{scikit-learn-contrib} supported project.
+Furthermore, it is fully compatible with \texttt{scikit-learn}.% and is part of the \texttt{scikit-learn-contrib} supported project.
 Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
@@
 \noindent\textit{Project relevance} At the edition time, the repository is visited no less than $2,000$ per week, attracting about $300$ unique visitors per week.
-Additionally, the toolbox is supported by \texttt{scikit-learn} through the \texttt{scikit-learn-contrib} projects.
+%Additionally, the toolbox is supported by \texttt{scikit-learn} through the \texttt{scikit-learn-contrib} projects.
 

### 2016-06-27 main.tex

@@
         \addr{Department of Mathematics, University of Patras} \\ 
-        \addr{University Campus, GR-26110 Patras, Greece}} 
+        \addr{University Campus, 26504 Patras, Greece}} 
 \editor{-}
@@
 
-from unbalanced_dataset.over_sampling import SMOTE
+from imblearn.over_sampling import SMOTE
 
@@
 The implementation relies on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn}.
-Each class implements 3 main methods inspired from the \texttt{scikit-learn} API:
+Each sampler class implements three main methods inspired from the \texttt{scikit-learn} API:
 (i) \texttt{fit} computes the parameter values which are later needed to resample the data into a balanced set;
@@
 and (iii) \texttt{fit\_sample} is equivalent to calling the method \texttt{fit} followed by the method \texttt{sample}.
-A class \texttt{Pipeline} is inherited from \texttt{scikit-learn} toolbox to automatically combine \texttt{sampler}, \texttt{transformers}, and \texttt{estimators}.
+A class \texttt{Pipeline} is inherited from \texttt{scikit-learn} toolbox to automatically combine \texttt{samplers}, \texttt{transformers}, and \texttt{estimators}.
 

### 2016-06-27 main.tex
Add future works and stop to 5 pages

@@
 from sklearn.decomposition import PCA
-
 from imblearn.over_sampling import SMOTE
@@
 # Generate the dataset
-X, y = make_classification(n_classes=2, class_sep=2, weights=[0.1, 0.9],
-                           n_informative=3, n_redundant=1, flip_y=0,
-                           n_features=20, n_clusters_per_class=1,
-                           n_samples=5000, random_state=10)
+X, y = make_classification(n_classes=2, weights=[0.1, 0.9],
+                           n_features=20, n_samples=5000)
 
@@
 \begin{equation}
-r_{\chi} = \frac{|\chi_{min}|}{|\chi_{majB}|} \ ,
+r_{\chi} = \frac{|\chi_{min}|}{|\chi_{maj}|} \ ,
 \end{equation}
@@
 Two methods are currently available: (i) \texttt{Random over-sampling} is performed by randomly replicating the samples of $\chi_{min}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$ and \texttt{SMOTE} which randomly generate new samples between tuple of nearest neighbours of $\chi_{min}$~\citep{chawla2002smote}.
-Different variants of this algorithm have been proposed: \texttt{SMOTE borderline 1 \& 2}~\citep{han2005borderline} and \texttt{SMOTE SVM}~\citep{nguyen2011borderline}
+Different variants of this algorithm have been proposed: \texttt{SMOTE borderline 1 \& 2}~\citep{han2005borderline} and \texttt{SMOTE SVM}~\citep{nguyen2011borderline}.
 
@@
 The former is based on iteratively applying the \texttt{random under-sampling} method to build several sets, each of them with a desired balancing ratio $r_{\chi_{res}}$.
-The latter differs from the former in that a classifier is used at each iteration to determine the class of the randomly selected samples.
+The latter differs such that a classifier is used at each iteration to determine the class of the randomly selected samples.
 Misclassified samples are kept and propagated in the next subset.
@@
 
-\section{Conclusion}
+\section{Future plans and conclusion}
 
 In this paper, we shortly presented the foundations of the \texttt{imbalanced-learn} toolbox vision and API.
+As avenues for future works, additional methods based on prototype/instance selection, generation, and reduction will be added as well as additional user guides.
 

### 2016-06-29 cover_letter.tex
Add cover letter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thin Formal Letter
% LaTeX Template
% Version 1.11 (8/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% WikiBooks (http://en.wikibooks.org/wiki/LaTeX/Letters)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{letter}

% Adjust margins for aesthetics
\addtolength{\voffset}{-0.5in}
\addtolength{\hoffset}{-0.3in}
\addtolength{\textheight}{2cm}

%\longindentation=0pt % Un-commenting this line will push the closing "Sincerely," to the left of the page

%----------------------------------------------------------------------------------------
%YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\signature{G. Lemaitre, F. Nogueira, and C. Aridas} % Your name for the signature at the bottom

\address{12 rue de la Fonderie \\ 71200 Le Creusot \\ +33(0)761104782} % Your address and phone number

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Editor of JMLR} % Name/title of the addressee

%----------------------------------------------------------------------------------------
%LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{\textbf{Dear Sir or Madam,}}

This submission is intended for the machine learning open source software section.
Our software is a Python library to tackle the curse of imbalanced datasets in machine learning.
The recent popularity of this project strengthen us in our decision of disseminating the proposed package. 
This toolbox is released under an open source MIT license and is hosted in GitHub:

\texttt{https://github.com/fmfn/UnbalancedDataset}

The attached version to be reviewed is the \texttt{0.1} release and is also attached in a \texttt{tar.gz} archive.
A five pages description of the software is also provided emphasizing on the benefit of this software for machine learning application as well as the project vision.

Thank you for your time and consideration.

We look forward to your reply.

\vspace{2\parskip} % Extra whitespace for aesthetics
\closing{Sincerely,}
\vspace{2\parskip} % Extra whitespace for aesthetics

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}

### 2016-06-29 lemaitre2016a.tex
Add cover letter

--- 2016-06-27 main.tex
@@
 % Heading arguments are {volume}{year}{pages}{submitted}{published}{author-full-names}
-\jmlrheading{7}{2016}{1-5}{7/16}{-}{Guillaume Lema\^itre, Fernando Nogueira, Dayvid V. R. Oliveira and Christos K. Aridas}
+\jmlrheading{7}{2016}{1-5}{7/16}{-}{Guillaume Lema\^itre, Fernando Nogueira, 
+%Dayvid V. R. Oliveira - removing my name.
+and Christos K. Aridas}
 
 % Short headings should be running head and authors last names
-\ShortHeadings{A python toolbox to tackle the curse of imbalanced datasets in machine learning}{Lema\^itre, Nogueira, Oliveira, and Aridas}
+\ShortHeadings{A Python Toolbox to Tackle the Curse of Imbalanced Datasets in Machine Learning}{Lema\^itre, Nogueira, and Aridas}
 \firstpageno{1}
@@
 
-\title{A python toolbox to tackle the curse of imbalanced datasets in machine learning}
+\title{A Python Toolbox to Tackle the Curse of Imbalanced Datasets in Machine Learning}
 \author{Guillaume Lema\^itre \email g.lemaitre58@gmail.com \\ 
@@
         \addr{500 King Street West 4\textsuperscript{th} Floor Toronto, Ontario M5V1L9 Canada}
-        \AND
-        Dayvid V. R. Oliveira \email dvro@cin.ufpe.br \\ 
-        \addr{VIISAR Research Group, Centro de Inform\'atica - Universidade Federal de Pernambuco} \\ 
-        %\addr{Av. Prof. Luiz Freire, s/n - Cidade Universitária Recife - PE, 50740-540, Brazil}} 
-        \addr{Av. Jornalista Aníbal Fernandes, s/n - Cidade Universitária - PE, 50740-560, Brazil}
+        % REMOVING MY NAME AS COAUTHOR
+        %\AND
+        %Dayvid V. R. Oliveira \email dvro@cin.ufpe.br \\ 
+        %\addr{VIISAR Research Group, Centro de Inform\'atica - Universidade Federal de Pernambuco} \\ 
+        %%\addr{Av. Prof. Luiz Freire, s/n - Cidade Universitária Recife - PE, 50740-540, Brazil}} 
+        %\addr{Av. Jornalista Aníbal Fernandes, s/n - Cidade Universitária - PE, 50740-560, Brazil}
         \AND
@@
 
-\begin{abstract}
+\begin{abstract}%
 \texttt{imbalanced-learn} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.

### 2016-07-09 lemaitre2016a.tex
Update affiliation
Update the cover letter and manuscript

@@
 \author{Guillaume Lema\^itre \email g.lemaitre58@gmail.com \\ 
-    \addr{LE2I UMR6306, CNRS, Arts et M\'etiers, Universit\'e Bourgogne Franche-Comt\'e} \\ 
+    \addr{LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e} \\ 
     \addr{12 rue de la Fonderie, 71200 Le Creusot, France} \\ 
@@
         Christos K. Aridas \email char@upatras.gr \\ 
-        \addr{Department of Mathematics, University of Patras} \\ 
+        \addr{University of Patras} \\ 
         \addr{University Campus, 26504 Patras, Greece}} 
@@
 
-\noindent\textit{Quality insurance} In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1 of the toolbox.
+\noindent\textit{Quality insurance} In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1.1 of the toolbox.
 Furthermore, the code consistency is ensured by following \texttt{PEP8} standards and each new contribution is automatically checked through landscape, which provides metrics related to code quality.

### 2016-07-19 lemaitre2016a.tex
Change the release version

@@
 The proposed toolbox only depends on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
-Furthermore, it is fully compatible with \texttt{scikit-learn}.% and is part of the \texttt{scikit-learn-contrib} supported project.
+Furthermore, it is fully compatible with \texttt{scikit-learn} and is part of the \texttt{scikit-learn-contrib} supported project.
 Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
@@
 
-\noindent\textit{Quality insurance} In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1.1 of the toolbox.
+\noindent\textit{Quality insurance} In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1.3 of the toolbox.
 Furthermore, the code consistency is ensured by following \texttt{PEP8} standards and each new contribution is automatically checked through landscape, which provides metrics related to code quality.
@@
 \noindent\textit{Project relevance} At the edition time, the repository is visited no less than $2,000$ per week, attracting about $300$ unique visitors per week.
-%Additionally, the toolbox is supported by \texttt{scikit-learn} through the \texttt{scikit-learn-contrib} projects.
+Additionally, the toolbox is supported by \texttt{scikit-learn} through the \texttt{scikit-learn-contrib} projects.
 

### 2016-07-19 lemaitre2016a.tex
Update the github address

@@
 Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
-The toolbox is publicly available in GitHub \url{https://github.com/fmfn/UnbalancedDataset}.
+The toolbox is publicly available in GitHub \url{https://github.com/scikit-learn-contrib/imbalanced-learn}.
 \end{abstract}
@@
 \noindent\textit{Documentation} A consistent API documentation is provided using \texttt{sphinx} and \texttt{numpydoc}.
-An additional installation guide and examples are also provided and centralized on GitHub\footnote{\url{http://fmfn.github.io/UnbalancedDataset/}}.
+An additional installation guide and examples are also provided and centralized on GitHub\footnote{\url{https://github.com/scikit-learn-contrib/imbalanced-learn}}.
 

### 2016-09-21 lemaitre2016a.tex
Update the affiliation of Fernando
update the title

@@
 % Short headings should be running head and authors last names
-\ShortHeadings{A Python Toolbox to Tackle the Curse of Imbalanced Datasets in Machine Learning}{Lema\^itre, Nogueira, and Aridas}
+\ShortHeadings{Imbalanced-learn: A Python Toolbox to Tackle the Curse of Imbalanced Datasets in Machine Learning}{Lema\^itre, Nogueira, and Aridas}
 \firstpageno{1}
@@
         Fernando Nogueira \email fmfnogueira@gmail.com \\ 
-        \addr{theScore, Inc.} \\ 
-        \addr{500 King Street West 4\textsuperscript{th} Floor Toronto, Ontario M5V1L9 Canada}
+        \addr{ShoppeAI} \\ 
+        \addr{488 Wellington Street West, Suite 304, Toronto, Ontario M5V 1E3, Canada}
         % REMOVING MY NAME AS COAUTHOR

### 2016-09-21 lemaitre2016a.tex
Update the release number

@@
 
-\noindent\textit{Quality insurance} In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1.3 of the toolbox.
+\noindent\textit{Quality insurance} In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1.8 of the toolbox.
 Furthermore, the code consistency is ensured by following \texttt{PEP8} standards and each new contribution is automatically checked through landscape, which provides metrics related to code quality.

### 2016-09-21 lemaitre2016a.tex
Update the title

@@
 % Short headings should be running head and authors last names
-\ShortHeadings{Imbalanced-learn: A Python Toolbox to Tackle the Curse of Imbalanced Datasets in Machine Learning}{Lema\^itre, Nogueira, and Aridas}
+\ShortHeadings{A Python Toolbox to Tackle the Curse of Imbalanced Datasets in Machine Learning}{Lema\^itre, Nogueira, and Aridas}
 \firstpageno{1}
@@
 
-\title{A Python Toolbox to Tackle the Curse of Imbalanced Datasets in Machine Learning}
+\title{Imbalanced-learn: A Python Toolbox to Tackle the Curse of Imbalanced Datasets in Machine Learning}
 \author{Guillaume Lema\^itre \email g.lemaitre58@gmail.com \\ 

### 2016-11-08 lemaitre2016a.tex
Make correction for the reviewer 1

@@
 % Heading arguments are {volume}{year}{pages}{submitted}{published}{author-full-names}
-\jmlrheading{7}{2016}{1-5}{7/16}{-}{Guillaume Lema\^itre, Fernando Nogueira, 
+\jmlrheading{17}{2016}{1-5}{7/16; Revised 7/16}{11/2016}{Guillaume Lema\^itre, Fernando Nogueira, 
 %Dayvid V. R. Oliveira - removing my name.
@@
         \addr{University Campus, 26504 Patras, Greece}} 
-\editor{-}
+\editor{Geoff Holmes}
 
@@
 Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
-The toolbox is publicly available in GitHub \url{https://github.com/scikit-learn-contrib/imbalanced-learn}.
+The toolbox is publicly available in GitHub \\ \url{https://github.com/scikit-learn-contrib/imbalanced-learn}.
 \end{abstract}
@@
 
-\noindent\textit{Quality insurance} In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1.8 of the toolbox.
+\noindent\textit{Quality assurance} In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1.8 of the toolbox.
 Furthermore, the code consistency is ensured by following \texttt{PEP8} standards and each new contribution is automatically checked through landscape, which provides metrics related to code quality.
@@
 
-Let $\chi$ an imbalanced dataset with $\chi_{min}$ and $\chi_{maj}$ being the subset of samples belonging to the minority and majority class, respectively.
+Let $\chi$ be an imbalanced dataset with $\chi_{min}$ and $\chi_{maj}$ being the subset of samples belonging to the minority and majority class, respectively.
 The balancing ratio of the dataset $\chi$ is defined as:
@@
 
-In the contrary to the previous methods, \emph{cleaning under-sampling} do not allow to reach specifically the balancing ratio $r_{\chi_{res}}$, but rather clean the feature space based on some empirical criteria.
+Contrary to the previous methods, \emph{cleaning under-sampling} do not allow to reach specifically the balancing ratio $r_{\chi_{res}}$, but rather clean the feature space based on some empirical criteria.
 These criteria are derived from the nearest neighbours rule, namely: (i) \texttt{condensed nearest neighbours}~\citep{hart1968condensed}, (ii) \texttt{edited nearest neighbours}~\citep{wilson1972asymptotic}, (iii) \texttt{one-sided selection}~\citep{kubat1997addressing}, (iv) \texttt{neighbourhood cleaning rule}~\citep{laurikkala2001improving}, and (v) \texttt{Tomek links}~\citep{tomek1976two}.
@@
 
-In the contrary to under-sampling, data balancing can be performed by over-sampling such that new samples are generated in $\chi_{min}$ to reach the balancing ratio $r_{\chi_{res}}$.
+Contrary to under-sampling, data balancing can be performed by over-sampling such that new samples are generated in $\chi_{min}$ to reach the balancing ratio $r_{\chi_{res}}$.
 Two methods are currently available: (i) \texttt{Random over-sampling} is performed by randomly replicating the samples of $\chi_{min}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$ and \texttt{SMOTE} which randomly generate new samples between tuple of nearest neighbours of $\chi_{min}$~\citep{chawla2002smote}.

### 2016-11-08 lemaitre2016a.tex
Try to create a table

@@
 \usepackage{color}
+\usepackage{booktabs}
+\usepackage{tabularx}
+\usepackage{pifont}
+
+\newcommand{\cmark}{\ding{51}}
+\newcommand{\xmark}{\ding{55}}
 
@@
 
+\begin{table}
+  \centering
+  \scriptsize
+   \begin{tabular}{lcccc}
+    \toprule
+    \textbf{Method} & \multicolumn{2}{c}{\textbf{Over-sampling}} & \multicolumn{2}{c}{\textbf{Under-sampling}} \\
+    \cmidrule(lr){2-3}\cmidrule(lr){4-5}
+    & Binary & Mutli-class & Binary & Multiclass \\
+    \midrule
+    ADASYN~\citep{he2008adasyn} & \cmark & \xmark & \xmark & \xmark \\
+    SMOTE~\citep{chawla2002smote,han2005borderline,nguyen2011borderline} & \cmark & \xmark & \xmark & \xmark \\
+    ROS & \cmark & \cmark & \xmark & \xmark \\
+    CC & \xmark & \xmark & \cmark & \cmark \\
+    CNN~\citep{hart1968condensed} & \xmark & \xmark & \cmark & \cmark \\
+    ENN~\citep{wilson1972asymptotic} & \xmark & \xmark & \cmark & \cmark \\
+    RENN & \xmark & \xmark & \cmark & \cmark \\
+    AKNN & \xmark & \xmark & \cmark & \cmark \\
+    NM~\citep{mani2003knn} & \xmark & \xmark & \cmark & \cmark \\
+    NCL~\citep{laurikkala2001improving} & \xmark & \xmark & \cmark & \cmark \\
+    OSS~\citep{kubat1997addressing} & \xmark & \xmark & \cmark & \cmark \\
+    RUS & \xmark & \xmark & \cmark & \cmark \\
+    IHT~\citep{smith2014instance} & \xmark & \xmark & \cmark & \xmark \\
+    TL~\citep{tomek1976two} & \xmark & \xmark & \cmark & \xmark \\
+    BC~\citep{liu2009exploratory} & \xmark & \xmark & \cmark & \xmark \\
+    EE~\citep{liu2009exploratory} & \xmark & \xmark & \cmark & \cmark \\
+    SMOTE + ENN~\citep{batista2003balancing} & \cmark & \xmark & \cmark & \xmark \\
+    SMOTE + TL~\citep{batista2003balancing} & \cmark & \xmark & \cmark & \xmark \\
+    \bottomrule
+  \end{tabular}
+  \label{tab:imbmethods}
+\end{table}
+
 \subsection{Notation and background}
@@
 \emph{Fixed under-sampling} refer to the methods which perform under-sampling to obtain the appropriate balancing ratio $r_{\chi_{res}}$.
-The implemented methods perform the under-sampling based on different criteria such as: (i) random selection, (ii) clustering, (iii) nearest neighbours rule (i.e., \texttt{NearMiss}~\citep{mani2003knn}), and (iv) classification accuracy (i.e., \texttt{instance hardness threshold}~\citep{smith2014instance}).
+%The implemented methods perform the under-sampling based on different criteria such as: (i) random selection, (ii) clustering, (iii) nearest neighbours rule (i.e., \texttt{NearMiss}~\citep{mani2003knn}), and (iv) classification accuracy (i.e., \texttt{instance hardness threshold}~\citep{smith2014instance}).
 
 Contrary to the previous methods, \emph{cleaning under-sampling} do not allow to reach specifically the balancing ratio $r_{\chi_{res}}$, but rather clean the feature space based on some empirical criteria.
-These criteria are derived from the nearest neighbours rule, namely: (i) \texttt{condensed nearest neighbours}~\citep{hart1968condensed}, (ii) \texttt{edited nearest neighbours}~\citep{wilson1972asymptotic}, (iii) \texttt{one-sided selection}~\citep{kubat1997addressing}, (iv) \texttt{neighbourhood cleaning rule}~\citep{laurikkala2001improving}, and (v) \texttt{Tomek links}~\citep{tomek1976two}.
+%These criteria are derived from the nearest neighbours rule, namely: (i) \texttt{condensed nearest neighbours}~\citep{hart1968condensed}, (ii) \texttt{edited nearest neighbours}~\citep{wilson1972asymptotic}, (iii) \texttt{one-sided selection}~\citep{kubat1997addressing}, (iv) \texttt{neighbourhood cleaning rule}~\citep{laurikkala2001improving}, and (v) \texttt{Tomek links}~\citep{tomek1976two}.
 
@@
 Contrary to under-sampling, data balancing can be performed by over-sampling such that new samples are generated in $\chi_{min}$ to reach the balancing ratio $r_{\chi_{res}}$.
-Two methods are currently available: (i) \texttt{Random over-sampling} is performed by randomly replicating the samples of $\chi_{min}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$ and \texttt{SMOTE} which randomly generate new samples between tuple of nearest neighbours of $\chi_{min}$~\citep{chawla2002smote}.
-Different variants of this algorithm have been proposed: \texttt{SMOTE borderline 1 \& 2}~\citep{han2005borderline} and \texttt{SMOTE SVM}~\citep{nguyen2011borderline}.
+%Two methods are currently available: (i) \texttt{Random over-sampling} is performed by randomly replicating the samples of $\chi_{min}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$ and \texttt{SMOTE} which randomly generate new samples between tuple of nearest neighbours of $\chi_{min}$~\citep{chawla2002smote}.
+%Different variants of this algorithm have been proposed: \texttt{SMOTE borderline 1 \& 2}~\citep{han2005borderline} and \texttt{SMOTE SVM}~\citep{nguyen2011borderline}.
 
@@
 
-\texttt{SMOTE} over-sampling can lead to over-fitting which can be avoided by applying cleaning under-sampling methods~\citep{prati2009data}.
-In that regard, \cite{batista2003balancing} combined \texttt{SMOTE} either with \texttt{Tomek links} or \texttt{edited nearest neighbours}.
+Over-sampling can lead to over-fitting which can be avoided by applying cleaning under-sampling methods~\citep{prati2009data}.
+
+%\texttt{SMOTE} over-sampling can lead to over-fitting which can be avoided by applying cleaning under-sampling methods~\citep{prati2009data}.
+%In that regard, \cite{batista2003balancing} combined \texttt{SMOTE} either with \texttt{Tomek links} or \texttt{edited nearest neighbours}.
 
@@
 In fact, an ensemble of balanced sets is created and used to later train any classifier.
-Two methods are available to build such ensemble proposed by~\cite{liu2009exploratory}: \texttt{EasyEnsemble} and \texttt{BalanceCascade}.
-The former is based on iteratively applying the \texttt{random under-sampling} method to build several sets, each of them with a desired balancing ratio $r_{\chi_{res}}$.
-The latter differs such that a classifier is used at each iteration to determine the class of the randomly selected samples.
-Misclassified samples are kept and propagated in the next subset.
+%Two methods are available to build such ensemble proposed by~\cite{liu2009exploratory}: \texttt{EasyEnsemble} and \texttt{BalanceCascade}.
+%The former is based on iteratively applying the \texttt{random under-sampling} method to build several sets, each of them with a desired balancing ratio $r_{\chi_{res}}$.
+%The latter differs such that a classifier is used at each iteration to determine the class of the randomly selected samples.
+%Misclassified samples are kept and propagated in the next subset.
 

### 2016-11-08 lemaitre2016a.tex
Try to create a table
Change paragraph environment

@@
         Christos K. Aridas \email char@upatras.gr \\ 
+        \addr{Computational Intelligence Laboratory} \\
+        \addr{Department of Mathematics} \\ 
         \addr{University of Patras} \\ 
-        \addr{University Campus, 26504 Patras, Greece}} 
+        \addr{GR-26504 Patras, Greece}} 
 \editor{Geoff Holmes}
@@
 
-\subsection{Under-sampling}
-
+\paragraph{Under-sampling}
 Under-sampling refers to the process of reducing the number of samples in $\chi_{maj}$.
@@
 
-\subsection{Over-sampling}
-
+\paragraph{Over-sampling}
 Contrary to under-sampling, data balancing can be performed by over-sampling such that new samples are generated in $\chi_{min}$ to reach the balancing ratio $r_{\chi_{res}}$.
@@
 
-\subsection{Combination of over- and under-sampling}
-
+\paragraph{Combination of over- and under-sampling}
 Over-sampling can lead to over-fitting which can be avoided by applying cleaning under-sampling methods~\citep{prati2009data}.
@@
 
-\subsection{Ensemble learning}
-
+\paragraph{Ensemble learning}
 Under-sampling methods imply that samples of the majority class are lost during the balancing procedure.

### 2016-12-27 16-365.tex
Last modif

--- 2016-11-08 lemaitre2016a.tex
@@
 % Heading arguments are {volume}{year}{pages}{submitted}{published}{author-full-names}
-\jmlrheading{17}{2016}{1-5}{7/16; Revised 7/16}{11/2016}{Guillaume Lema\^itre, Fernando Nogueira, 
-%Dayvid V. R. Oliveira - removing my name.
+\jmlrheading{17}{2016}{1-5}{7/16; Revised 7/16}{11/16}{Guillaume Lema\^itre, Fernando Nogueira,
+  % Dayvid V. R. Oliveira - removing my name.
   and Christos K. Aridas}
@@
 \title{Imbalanced-learn: A Python Toolbox to Tackle the Curse of Imbalanced Datasets in Machine Learning}
-\author{Guillaume Lema\^itre \email g.lemaitre58@gmail.com \\ 
-    \addr{LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e} \\ 
-    \addr{12 rue de la Fonderie, 71200 Le Creusot, France} \\ 
-    \addr{ViCOROB, Universitat de Girona} \\ 
-    \addr{Campus Montilivi, Edifici P4, 17071 Girona, Spain}
+\author{Guillaume Lema\^itre \email guillaume.lemaitre@inria.fr \\
+  \addr{Parietal team, Inria, CEA, Universit\'e Paris-Saclay} \\
+  \addr{1 Rue Honor\'e d'Estienne d'Orves, 91120 Palaiseau, France}
   \AND
@@
   % REMOVING MY NAME AS COAUTHOR
-        %\AND
-        %Dayvid V. R. Oliveira \email dvro@cin.ufpe.br \\ 
-        %\addr{VIISAR Research Group, Centro de Inform\'atica - Universidade Federal de Pernambuco} \\ 
-        %%\addr{Av. Prof. Luiz Freire, s/n - Cidade Universitária Recife - PE, 50740-540, Brazil}} 
-        %\addr{Av. Jornalista Aníbal Fernandes, s/n - Cidade Universitária - PE, 50740-560, Brazil}
+  % \AND
+  % Dayvid V. R. Oliveira \email dvro@cin.ufpe.br \\
+  % \addr{VIISAR Research Group, Centro de Inform\'atica - Universidade Federal de Pernambuco} \\
+  %% \addr{Av. Prof. Luiz Freire, s/n - Cidade Universitária Recife - PE, 50740-540, Brazil}}
+  % \addr{Av. Jornalista Aníbal Fernandes, s/n - Cidade Universitária - PE, 50740-560, Brazil}
   \AND
   Christos K. Aridas \email char@upatras.gr \\
-        \addr{Computational Intelligence Laboratory} \\
-        \addr{Department of Mathematics} \\ 
   \addr{University of Patras} \\
-        \addr{GR-26504 Patras, Greece}} 
+  \addr{University Campus, 26504 Patras, Greece}}
 \editor{Geoff Holmes}
@@
 
-\noindent\textit{Quality assurance} In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.1.8 of the toolbox.
+\noindent\textit{Quality assurance} In order to ensure code quality, a set of unit tests is provided leading to a coverage of 99 \% for the release 0.2 of the toolbox.
 Furthermore, the code consistency is ensured by following \texttt{PEP8} standards and each new contribution is automatically checked through landscape, which provides metrics related to code quality.
@@
 and (iii) \texttt{fit\_sample} is equivalent to calling the method \texttt{fit} followed by the method \texttt{sample}.
-A class \texttt{Pipeline} is inherited from \texttt{scikit-learn} toolbox to automatically combine \texttt{samplers}, \texttt{transformers}, and \texttt{estimators}.
+A class \texttt{Pipeline} is inherited from \texttt{scikit-learn}
+toolbox to automatically combine \texttt{samplers},
+\texttt{transformers}, and \texttt{estimators}.
+Additionally, we provide some specific state-of-the-art metrics to evaluate
+classification performance.
 
@@
 The implemented methods can be categorized into 2 groups: (i) fixed under-sampling and (ii) cleaning under-sampling.
-
 \emph{Fixed under-sampling} refer to the methods which perform under-sampling to obtain the appropriate balancing ratio $r_{\chi_{res}}$.
-%The implemented methods perform the under-sampling based on different criteria such as: (i) random selection, (ii) clustering, (iii) nearest neighbours rule (i.e., \texttt{NearMiss}~\citep{mani2003knn}), and (iv) classification accuracy (i.e., \texttt{instance hardness threshold}~\citep{smith2014instance}).
-
+% The implemented methods perform the under-sampling based on different criteria such as: (i) random selection, (ii) clustering, (iii) nearest neighbours rule (i.e., \texttt{NearMiss}~\citep{mani2003knn}), and (iv) classification accuracy (i.e., \texttt{instance hardness threshold}~\citep{smith2014instance}).
 Contrary to the previous methods, \emph{cleaning under-sampling} do not allow to reach specifically the balancing ratio $r_{\chi_{res}}$, but rather clean the feature space based on some empirical criteria.
-%These criteria are derived from the nearest neighbours rule, namely: (i) \texttt{condensed nearest neighbours}~\citep{hart1968condensed}, (ii) \texttt{edited nearest neighbours}~\citep{wilson1972asymptotic}, (iii) \texttt{one-sided selection}~\citep{kubat1997addressing}, (iv) \texttt{neighbourhood cleaning rule}~\citep{laurikkala2001improving}, and (v) \texttt{Tomek links}~\citep{tomek1976two}.
-
+% These criteria are derived from the nearest neighbours rule, namely: (i) \texttt{condensed nearest neighbours}~\citep{hart1968condensed}, (ii) \texttt{edited nearest neighbours}~\citep{wilson1972asymptotic}, (iii) \texttt{one-sided selection}~\citep{kubat1997addressing}, (iv) \texttt{neighbourhood cleaning rule}~\citep{laurikkala2001improving}, and (v) \texttt{Tomek links}~\citep{tomek1976two}.
 % Under-sampling refers to the process of reducing the number of samples in $\chi_{maj}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$.
 % The following methods are considered to perform such balancing.
-
 % \texttt{Random under-sampling} is performed by randomly selecting without replacement a subset of samples from $\chi_{maj}$ to obtain the desired balancing ratio $r_{\chi_{res}}$.
-
 % \texttt{Cluster centroids method} refers to the use of a $k$-means to cluster the feature space.
@@
 % Note that the samples in $\chi_{res_{maj}}$ do not correspond to the original samples of $\chi_{maj}$ and are synthetically generated.
-
 % \texttt{Condensed nearest neighbours} \citep{hart1968condensed}
-
 % \texttt{Edited nearest neighbours} \citep{wilson1972asymptotic}
-
 % \texttt{Instance hardness threshold} \citep{smith2014instance}
-
 % \texttt{NearMiss} offers three different methods to under-sample the majority class~\citep{mani2003knn}.
@@
 Contrary to under-sampling, data balancing can be performed by over-sampling such that new samples are generated in $\chi_{min}$ to reach the balancing ratio $r_{\chi_{res}}$.
-%Two methods are currently available: (i) \texttt{Random over-sampling} is performed by randomly replicating the samples of $\chi_{min}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$ and \texttt{SMOTE} which randomly generate new samples between tuple of nearest neighbours of $\chi_{min}$~\citep{chawla2002smote}.
-%Different variants of this algorithm have been proposed: \texttt{SMOTE borderline 1 \& 2}~\citep{han2005borderline} and \texttt{SMOTE SVM}~\citep{nguyen2011borderline}.
+% Two methods are currently available: (i) \texttt{Random over-sampling} is performed by randomly replicating the samples of $\chi_{min}$ to obtain the appropriate balancing ratio $r_{\chi_{res}}$ and \texttt{SMOTE} which randomly generate new samples between tuple of nearest neighbours of $\chi_{min}$~\citep{chawla2002smote}.
+% Different variants of this algorithm have been proposed: \texttt{SMOTE borderline 1 \& 2}~\citep{han2005borderline} and \texttt{SMOTE SVM}~\citep{nguyen2011borderline}.
 
@@
 
-%\texttt{SMOTE} over-sampling can lead to over-fitting which can be avoided by applying cleaning under-sampling methods~\citep{prati2009data}.
-%In that regard, \cite{batista2003balancing} combined \texttt{SMOTE} either with \texttt{Tomek links} or \texttt{edited nearest neighbours}.
+% \texttt{SMOTE} over-sampling can lead to over-fitting which can be avoided by applying cleaning under-sampling methods~\citep{prati2009data}.
+% In that regard, \cite{batista2003balancing} combined \texttt{SMOTE} either with \texttt{Tomek links} or \texttt{edited nearest neighbours}.
 
@@
 In fact, an ensemble of balanced sets is created and used to later train any classifier.
-%Two methods are available to build such ensemble proposed by~\cite{liu2009exploratory}: \texttt{EasyEnsemble} and \texttt{BalanceCascade}.
-%The former is based on iteratively applying the \texttt{random under-sampling} method to build several sets, each of them with a desired balancing ratio $r_{\chi_{res}}$.
-%The latter differs such that a classifier is used at each iteration to determine the class of the randomly selected samples.
-%Misclassified samples are kept and propagated in the next subset.
+% Two methods are available to build such ensemble proposed by~\cite{liu2009exploratory}: \texttt{EasyEnsemble} and \texttt{BalanceCascade}.
+% The former is based on iteratively applying the \texttt{random under-sampling} method to build several sets, each of them with a desired balancing ratio $r_{\chi_{res}}$.
+% The latter differs such that a classifier is used at each iteration to determine the class of the randomly selected samples.
+% Misclassified samples are kept and propagated in the next subset.
 

### 2016-12-27 response.tex
Last modif

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thin Formal Letter
% LaTeX Template
% Version 1.11 (8/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% WikiBooks (http://en.wikibooks.org/wiki/LaTeX/Letters)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% ----------------------------------------------------------------------------------------
% DOCUMENT CONFIGURATIONS
% ----------------------------------------------------------------------------------------

\documentclass{letter}

% Adjust margins for aesthetics
\addtolength{\voffset}{-0.5in}
\addtolength{\hoffset}{-0.3in}
\addtolength{\textheight}{2cm}

% \longindentation=0pt % Un-commenting this line will push the closing "Sincerely," to the left of the page

% ----------------------------------------------------------------------------------------
% YOUR NAME & ADDRESS SECTION
% ----------------------------------------------------------------------------------------

\signature{G. Lemaitre, F. Nogueira, and C. Aridas} % Your name for the signature at the bottom

\address{1 Rue Honor\'e d'Estienne d'Orves \\ 91120 Palaiseau \\ +33(0)761104782} % Your address and phone number

% ----------------------------------------------------------------------------------------

\begin{document}

% ----------------------------------------------------------------------------------------
% ADDRESSEE SECTION
% ----------------------------------------------------------------------------------------

\begin{letter}{Geoff Holmes \\ Action editor of JMLR} % Name/title of the addressee

  % ----------------------------------------------------------------------------------------
  % LETTER CONTENT SECTION
  % ----------------------------------------------------------------------------------------

  \opening{\textbf{Dear Sir,}}

  Alongside with the submission 16-365 at the MLOSS of the JMLR, we
  would

  This submission is intended for the machine learning open source software section.
  Our software is a Python library to tackle the curse of imbalanced datasets in machine learning.
  The recent popularity of this project strengthen us in our decision of disseminating the proposed package.
  This toolbox is released under an open source MIT license and is hosted in GitHub:

  \texttt{https://github.com/scikit-learn-contrib/imbalanced-learn}

  The attached version to be reviewed is the \texttt{0.1.3} release and is also attached in a \texttt{tar.gz} archive.
  A five pages description of the software is also provided emphasizing on the benefit of this software for machine learning application as well as the project vision.

  Thank you for your time and consideration.

  We look forward to your reply.

  \vspace{2\parskip} % Extra whitespace for aesthetics
  \closing{Sincerely,}
  \vspace{2\parskip} % Extra whitespace for aesthetics

  % ----------------------------------------------------------------------------------------

\end{letter}

\end{document}

### 2016-12-27 response.tex
Add the response to reviewer

@@
   Alongside with the submission 16-365 at the MLOSS of the JMLR, we
-  would
+  would like to thank the reviewers for their pertinent suggestions in
+  an effort to improve our software.
+  Therefore, we addressed the issues raised by the reviewers by
+  improving the manuscript, the documentation, and the software.
 
-  This submission is intended for the machine learning open source software section.
-  Our software is a Python library to tackle the curse of imbalanced datasets in machine learning.
-  The recent popularity of this project strengthen us in our decision of disseminating the proposed package.
-  This toolbox is released under an open source MIT license and is hosted in GitHub:
+  Below, we go into details regarding the changes which has been done:
 
-  \texttt{https://github.com/scikit-learn-contrib/imbalanced-learn}
+  \textbf{Reviewer \#1:}
 
-  The attached version to be reviewed is the \texttt{0.1.3} release and is also attached in a \texttt{tar.gz} archive.
-  A five pages description of the software is also provided emphasizing on the benefit of this software for machine learning application as well as the project vision.
+  \begin{itemize}
+  \item \textit{I believe that a real world example of this package
+      improving generalization performance would make the paper more
+      convincing.}\\
+    Due to the page limits, we did not added any real-world example in
+    the manuscript itself. However, examples have been added in the
+    documentation of the software. Additionally, we continuously aim
+    at adding real-world case studies.
+  \item \textit{Typos / phrasing suggestions.}\\
+    We addressed the typos and adopted the phrasing suggested.
+  \end{itemize}
+
+  \textbf{Reviewer \#2:}
+
+  \begin{itemize}
+  \item \textit{A table could be added with the implemented methods
+      grouped by type (over-sampling, under-sampling ...). The table
+      could also include a categorization of the methods concerning
+      the possibility of application only to two-class or multi-class
+      problems. This could provide a better overview of the
+      implemented methods.}\\
+    We simplified the description for each method and add the
+    suggested table indicating on which type of problems ---
+    binary \emph{vs.} multi-class --- the methods can be used.
+  \item \textit{It would help users with real world problems when
+      using the proposed toolbox.  Researchers and developers would
+      also benefit from this perspective.}\\
+    As previously mentioned, due to the page limits, we did not added
+    any real-world example in the manuscript itself. However, examples
+    have been added in the documentation of the
+    software. Additionally, we continuously aim at adding real-world
+    case studies.
+  \item \textit{There is an huge number of methods proposed to address
+      the problem of imbalanced domains.
+      The proposed toolbox includes several pre-processing methods and two
+      algorithm level methods (ensembles). This is on the short side in
+      terms of what is currently available.}\\
+    The implementation of additional methods is planned for the next
+    release of the toolbox and is currently in the issue tracker on
+    GitHub. We are striving to include these new methods within the
+    next 6 months.
+  \item \textit{For instance, an example could be provided for
+      studying the impact of using different parameters with a given
+      strategy.
+      The results could then be presented considering different performance
+      assessment metrics.  Given that the issue of performance assessment in
+      imbalanced domains is complex,  this example could also show how the
+      user may assess the performance in a new metric that is not
+      implemented in scikit-learn (for instance G-mean, dominance or Index
+      of Balanced Accuracy(IBA)).}\\
+    We implemented new metrics available in the \texttt{metrics}
+    modules of the toolbox. Sensitivity/specificity, geometric-mean,
+    and index of balanced accuracy have been added. Additionally, we
+    proposed a method to generate a classification report reporting
+    the different metrics. Furthermore, examples presenting the
+    metrics have been added to the documentation.
+  \item \textit{Another example could also be added considering a
+      real world data set. This example could be built to answer the
+      question:
+      ``What is the best strategy that I can use in this specific
+      problem?''} \\
+    We provide an example using a real-world dataset which
+    illustrate the empirical search for such purpose. A grid-search
+    using different balancing method in conjunction with a
+    classifier is performed.
+  \item \textit{Finally, a third example that considers a problem
+      with multiple classes could also be included.} \\
+    We introduce an example which illustrate the use of a method for
+    a multi-class problem and we additionally generate the according
+    classification report.
+  \item \textit{With respect to the references to implementations
+      available in R, the authors should eventually refer the
+      package UBL that is a specific R package for handling
+      imbalanced distributions, so it is probably the R package with
+      more similar objectives to the current one.} \\
+    We refer to this toolbox in the manuscript.
+  \end{itemize}
 

### 2016-12-31 16-365.tex
Last modif
Edit for the submission

@@
   Christos K. Aridas \email char@upatras.gr \\ 
+  \addr{Computational Intelligence Laboratory} \\
+  \addr{Department of Mathematics} \\ 
   \addr{University of Patras} \\ 
-  \addr{University Campus, 26504 Patras, Greece}}
+  \addr{GR-26504 Patras, Greece}} 
 \editor{Geoff Holmes}
@@
   \texttt{imbalanced-learn} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
-  The implemented state-of-the-art methods can be categorized into 4 groups: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
-  The proposed toolbox only depends on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
+  The implemented state-of-the-art methods can be categorized into four groups: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
+  The proposed toolbox depends only on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
   Furthermore, it is fully compatible with \texttt{scikit-learn} and is part of the \texttt{scikit-learn-contrib} supported project.
   Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
-  The toolbox is publicly available in GitHub \\ \url{https://github.com/scikit-learn-contrib/imbalanced-learn}.
+  The toolbox is publicly available on GitHub \\ \url{https://github.com/scikit-learn-contrib/imbalanced-learn}.
 \end{abstract}
@@
 telecommunication managements, bioinformatics, fraud detection, and medical diagnosis,
-and has been considered one of the top 10 problems in data mining and
+and has been considered one of the top ten problems in data mining and
 pattern recognition~\citep{yang200610,rastgoo2016tackling}.
@@
 approaches have been specifically proposed to handle such datasets.
-Such standalone methods have been implemented mainly in R language~\citep{torgo2010data,kuhn2015caret,dal2013racing}.
-Up to our knowledge, however, there is no python toolbox allowing such processing while cutting edge machine learning toolboxes are available~\citep{pedregosa2011scikit,sonnenburg2010shogun}.
+Some of these methods have been implemented mainly in R language~\citep{torgo2010data,kuhn2015caret,dal2013racing}.
+Up to our knowledge, there is no python toolbox allowing such processing while cutting edge machine learning toolboxes are available~\citep{pedregosa2011scikit,sonnenburg2010shogun}.
 
@@
   in machine learning}. The following sections present the project vision, a snapshot of the API, an overview of the implemented methods,
-and finally, the conclusion of this paper, including future functionalities
+and finally, we conclude this work by including future functionalities
 for the \texttt{imbalanced-learn} API.
@@
 
-\noindent\textit{Continuous integration} To allow user and developer to either use or contribute to this toolbox, Travis CI is used to easily integrate new code and ensure back-compatibility.
+\noindent\textit{Continuous integration} To allow both the user and the developer to either use or contribute to this toolbox, Travis CI is used to easily integrate new code and ensure back-compatibility.
 
@@
 
-\noindent\textit{Project relevance} At the edition time, the repository is visited no less than $2,000$ per week, attracting about $300$ unique visitors per week.
+\noindent\textit{Project relevance} At the edition time, the repository is visited no less than $2,000$ times per week, attracting about $300$ unique visitors per week.
 Additionally, the toolbox is supported by \texttt{scikit-learn} through the \texttt{scikit-learn-contrib} projects.
@@
 Each sampler class implements three main methods inspired from the \texttt{scikit-learn} API:
-(i) \texttt{fit} computes the parameter values which are later needed to resample the data into a balanced set;
+(i) \texttt{fit} computes several statistics which are later needed to resample the data into a balanced set;
 (ii) \texttt{sample} performs the sampling and returns the data with the desired balancing ratio;
 and (iii) \texttt{fit\_sample} is equivalent to calling the method \texttt{fit} followed by the method \texttt{sample}.
-A class \texttt{Pipeline} is inherited from \texttt{scikit-learn}
+A class \texttt{Pipeline} is inherited from the \texttt{scikit-learn}
 toolbox to automatically combine \texttt{samplers},
@@
 classification performance.
+
+\bigbreak
 

### 2016-12-31 16-365.tex

@@
   \texttt{imbalanced-learn} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
-  The implemented state-of-the-art methods can be categorized into four groups: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
+  The implemented state-of-the-art methods can be categorized into 4 groups: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
   The proposed toolbox depends only on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
@@
   Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
-  The toolbox is publicly available on GitHub \\ \url{https://github.com/scikit-learn-contrib/imbalanced-learn}.
+  Source code, binaries, and documentation can be downloaded from \url{https://github.com/scikit-learn-contrib/imbalanced-learn}.
 \end{abstract}
@@
 telecommunication managements, bioinformatics, fraud detection, and medical diagnosis,
-and has been considered one of the top ten problems in data mining and
+and has been considered one of the top 10 problems in data mining and
 pattern recognition~\citep{yang200610,rastgoo2016tackling}.
@@
 classification performance.
-
 \bigbreak
